### 2013-01-04 Article.tex
Criei o repositório e adicionei um esboço do artigo

%%%% ijcai11.tex

\typeout{IJCAI-13 Instructions for Authors}

% These are the instructions for authors for IJCAI-13.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{article}
% The file ijcai13.sty is the style file for IJCAI-13 (same as ijcai07.sty).
\usepackage{ijcai13}

% Use the postscript times font!
\usepackage{times}

\usepackage{latexsym}

\title{Social Computing Article\thanks{This title is temporary}}
\author{Tabajara, Lucas \\
Institute of Informatics \\
Federal University of Rio Grande do Sul\\
Brazil \\
lmtabajara@inf.ufrgs.br
\and
Prates, Marcelo \\
Institute of Informatics \\
Federal University of Rio Grande do Sul\\
Brazil \\
morprates@inf.ufrgs.br}

\begin{document}

\maketitle

\begin{abstract}
  Abstract
\end{abstract}

\section{Introduction}

Introduction

\section{Background}

Background

\section{Contribution}

Contribution

\section{Methodology}

Methodology

\section{Results}

Results

\section{Conclusions}

Conclusions

%% The file named.bst is a bibliography style file for BibTeX 0.99c
%%\bibliographystyle{named}
\bibliography{Article}

\end{document}

### 2013-01-04 Article.tex
Escrevi um pouco no campo da metodologia
É mais um esboço, tá sujeito a revisões e deleções

@@
 
-Methodology
+We developed a system in which the environment of the sudoku problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
+The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, giving a basis for the dynamics of the agent network.
+A {\em Memetic Network Algorithm} is composed of an ordered set of $N$ agents, each encoding a complete solution to the optimization problem, and a binary $N \times N$ matrix encoding possible connections between agents.
+Additionally, a {\em Memetic Network Algorithm} is composed of a set of rules specifying how connections between agents are formed and erased and how interactions between these agents take place.
+These rules are grouped under the categories of {\em Connection Rules}, specifying how agents will connect and disconnect from each other; {\em Aggregation Rules}, specifying the dynamics of the information flow through connections; and {\em Appropriation Rules}, specifying how agents are supposed to add local changes to the information received through their connections.
+
+Our solution adapts the {\em Memetic Newtork} technique - originally intended for use in optimization problems - to the context of constraint satisfaction problems.
+In this specific case (sudoku solving), we treat problems with one unique solution.
+To deal with this scenario, we propose a {\em Memetic Network} variation in which each agent encodes not a complete, but a partial solution to the problem.
+
+Our solution employs a fixed topology for the agent network and models cooperation through a set of {\em aggregation rules} and reasoning through a set of {\em appropriation rules}.
+Our aggregation rules specify how sudoku partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with sudoku solving techniques such as naked singles, swordfish, etc.
+
+\subsection{Aggregation Rules}
+
+The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings.
+For instance, the authors analysis has shown that users tend to copy not the most complete solutions, but instead the first solutions on the graphic interface.
+Additionally, we know from that same paper that users rarely copy solutions from more than 6 neighbours.
+In order to analyse and compare this behaviours, we developed a collection of aggregation rules, each modelling a copying strategy.
+
+\subsubsection{Pick Most Filled}
+
+This rule employs the intuitive strategy of copying from the neighbour with the most filled sudoku, namely the most complete solution
+
+\subsubsection{Pick Among First}
+
+We know that users tend to copy the first (from left to right) solutions on the graphic interface~\cite{farenzena:collabem}.
+The authors have provided us with a mathematical model of this behaviour, stated as $X(k) = (1-p)^{k-1}p$, where the parameter $p$ is fixed as $p = 0.5479$ and $X(k)$ denotes the probability of an agent copying the $k_{th}$ neighbour solution.
+
+We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent to compose a simulated graphic interface in which each agent visualizes some neighbours before or after others.
+Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ solution with probability $X(k)$.
+
+\subsection{Appropriation Rules}
+
+In sudoku strategy literature, as in chess, we find multiple techniques with iconic names.
+Some popular examples are {\em naked singles}, {\em naked twins}, {\em swordfish}.
+These strategies intend to, given a sudoku puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}".
+We reproduced a variety of these strategies, modelling each one of them as a function mapping a sudoku partial solution to a set of movements.
+
+\subsubsection{Only Choice}
+
+\subsubsection{Single Possibility}
+
+\subsubsection{Two out of Three}
+
+\subsubsection{Naked Twins}
 
@@
 %%\bibliographystyle{named}
-\bibliography{Article}
+\bibliography{Bibliography}
 

### 2013-01-05 Article.tex
Escrevi mais na metodologia e adicionei as referências

@@
 
-This rule employs the intuitive strategy of copying from the neighbour with the most filled sudoku, namely the most complete solution
+This rule employs the intuitive strategy of copying from the neighbour with the most filled sudoku, namely the most complete solution.
 
@@
 
+This technique proceeds to mark a sudoku cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.
+For instance, the {\em only choice} rule would mark cell $(1,2)$ with value $4$ in the below sudoku puzzle:
+
+\[ \left( \begin{array}{ccccccccc}
+  &   &   & 7 &   &   &   & 5 & 8 \\
+  & 5 & 6 & 2 & 1 & 8 & 7 & 9 & 3 \\
+  &   &   &   &   &   & 1 &   &   \\
+  &   &   &   &   &   &   & 8 & 1 \\
+  &   &   & 3 & 7 & 6 &   &   &   \\
+9 & 6 &   &   &   &   &   &   &   \\
+  &   & 5 &   &   &   &   &   &   \\
+  &   & 4 &   & 2 & 1 & 8 & 3 &   \\
+8 & 7 &   &   &   & 3 &   &   &   \end{array}  \right)\]
+
+\[ \left( \begin{array}{ccccccccc}
+  &   &   & 7 &   &   &   & 5 & 8 \\
+{\bf 4} & 5 & 6 & 2 & 1 & 8 & 7 & 9 & 3 \\
+  &   &   &   &   &   & 1 &   &   \\
+  &   &   &   &   &   &   & 8 & 1 \\
+  &   &   & 3 & 7 & 6 &   &   &   \\
+9 & 6 &   &   &   &   &   &   &   \\
+  &   & 5 &   &   &   &   &   &   \\
+  &   & 4 &   & 2 & 1 & 8 & 3 &   \\
+8 & 7 &   &   &   & 3 &   &   &   \end{array}  \right)\]
+
 \subsubsection{Single Possibility}
 
+This rule marks a sudoku cell with value $v$ only if $v$ is the single possible value to mark that cell.
+The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block.
+For instance, the {\em single possibility} rule would mark cell $(4,1)$ with value $7$ in the below sudoku puzzle, since the values $1$,$2$,$3$,$4$,$5$ and $8$ were already present in the cell's column (leaving the possibilities $6$,$7$ and $9$) and the values $6$ and $9$ were already present in the cells' row (leaving the single possibility $7$).
+
+\[ \left( \begin{array}{ccccccccc}
+8 & 2 & 5 & 6 & 3 & 1 & 9 & 7 & 4 \\
+  & 6 & 7 &   & 2 & 4 &   &   & 8 \\
+4 &   &   &   &   & 7 & 6 &   & 2 \\
+  & 5 & 9 &   & 4 & 8 & 2 & 6 & 1 \\
+1 &   & 8 & 2 & 6 & 9 & 7 & 4 & 5 \\
+  & 4 &   & 1 & 7 & 5 &   & 8 &   \\
+3 &   & 1 & 4 &   &   &   &   &   \\
+5 &   &   &   &   & 3 & 4 &   &   \\
+2 & 9 & 4 &   &   & 6 & 5 &   &   \end{array}  \right)\]
+
+\[ \left( \begin{array}{ccccccccc}
+8 & 2 & 5 & 6 & 3 & 1 & 9 & 7 & 4 \\
+  & 6 & 7 &   & 2 & 4 &   &   & 8 \\
+4 &   &   &   &   & 7 & 6 &   & 2 \\
+{\bf 7} & 5 & 9 &   & 4 & 8 & 2 & 6 & 1 \\
+1 &   & 8 & 2 & 6 & 9 & 7 & 4 & 5 \\
+  & 4 &   & 1 & 7 & 5 &   & 8 &   \\
+3 &   & 1 & 4 &   &   &   &   &   \\
+5 &   &   &   &   & 3 & 4 &   &   \\
+2 & 9 & 4 &   &   & 6 & 5 &   &   \end{array}  \right)\]
+
 \subsubsection{Two out of Three}
+
+This rule works on a group of three contiguous $3 \times 3$ blocks.
+It aims to find a value $v$ such that $v$ is present in two of the three $3 \times 3$ blocks encompassed by the group, but missing on the third.
+It then proceeds by enumerating all the candidate cells (namely the empty cells) on this block, and then eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks.
+If the resulting set has cardinality $1$, the rule has successfully found one cell to mark.
+For instance, the {\em two out of three} rule would mark cell $(2,9)$ with value $1$.
+
+\[ \left( \begin{array}{ccccccccc}
+  &   & 9 & 5 & 1 &   &   & 6 & 2 \\
+6 & 3 & 4 &   &   &   & 5 & 9 &   \\
+1 & 2 & 5 & 6 & 3 & 9 & 7 &   & 4 \\
+2 & 5 &   & 8 & 4 & 7 & 6 & 3 &   \\
+4 & 6 &   &   & 5 &   &   & 1 & 7 \\
+  & 8 & 7 & 3 & 6 & 1 &   & 2 & 5 \\
+5 &   & 6 & 1 & 7 & 3 & 2 & 4 & 8 \\
+  & 1 & 2 &   &   &   & 9 & 7 & 6 \\
+7 & 4 &   &   & 9 & 6 & 1 &   &   \end{array}  \right)\]
+
+\[ \left( \begin{array}{ccccccccc}
+  &   & 9 & 5 & 1 &   &   & 6 & 2 \\
+6 & 3 & 4 &   &   &   & 5 & 9 & {\bf 1} \\
+1 & 2 & 5 & 6 & 3 & 9 & 7 &   & 4 \\
+2 & 5 &   & 8 & 4 & 7 & 6 & 3 &   \\
+4 & 6 &   &   & 5 &   &   & 1 & 7 \\
+  & 8 & 7 & 3 & 6 & 1 &   & 2 & 5 \\
+5 &   & 6 & 1 & 7 & 3 & 2 & 4 & 8 \\
+  & 1 & 2 &   &   &   & 9 & 7 & 6 \\
+7 & 4 &   &   & 9 & 6 & 1 &   &   \end{array}  \right)\]
 
@@
 %% The file named.bst is a bibliography style file for BibTeX 0.99c
-%%\bibliographystyle{named}
-\bibliography{Bibliography}
+\bibliographystyle{named}
+\bibliography{Article}
 

### 2013-01-06 Article.tex
Fiz um esboço da introdução

@@
 
-Introduction
+For years multi-agent systems have been used to research cooperation as a tool for problem-solving.
+Recently, however, there has been an increasing interest in the use of human beings as problem-solving agents.
+Several studies have been conducted in which subjects are connected in a network with the goal of searching for the solution of a specific problem, and those have helped shed some light on the way humans interact in order to solve problems.
+
+The experiments conducted by \cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question.
+The behaviour observed in that study has provided evidence that human beings in a cooperative problem-solving environment might not evaluate solutions proposed by their peers, instead choosing the most readily available one.
+
+Another result of those observations is that there is a higher probability of individuals copying peers' solutions when those are shared by several neighbours, referred to as an evidence of \emph{conformist behaviour}.
+A similar behaviour was observed in \cite{mason:collablearnet} for a different problem.
+
+We have built a multi-agent system that simulates the experiments of \cite{farenzena:collabem} with the aim of verifying whether the strategies employed by humans are competitive with other heuristics.
+After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.
 

### 2013-01-06 Article.tex
Corrigi algumas coisas no meu texto, adicionei a referência pro mason e fiz o merge

@@
 
-\section{Methodology}
+\section{System Overview}
 
 We developed a system in which the environment of the sudoku problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
-The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, giving a basis for the dynamics of the agent network.
-A {\em Memetic Network Algorithm} is composed of an ordered set of $N$ agents, each encoding a complete solution to the optimization problem, and a binary $N \times N$ matrix encoding possible connections between agents.
+The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, providing a basis for the dynamics of the agent network.
+
+\section{Sudoku Solving Memetic Network}
+
+A {\em Memetic Network Algorithm} is composed of an ordered set of $N$ agents, each encoding a complete solution to the optimization problem, and a binary $N \times N$ matrix representing possible connections between agents.
 Additionally, a {\em Memetic Network Algorithm} is composed of a set of rules specifying how connections between agents are formed and erased and how interactions between these agents take place.
-These rules are grouped under the categories of {\em Connection Rules}, specifying how agents will connect and disconnect from each other; {\em Aggregation Rules}, specifying the dynamics of the information flow through connections; and {\em Appropriation Rules}, specifying how agents are supposed to add local changes to the information received through their connections.
+These rules are grouped under the categories of {\em Connection Rules}, specifying how agents will connect and disconnect from each other; {\em Aggregation Rules}, specifying the dynamics of the information flow through connections; and {\em Appropriation Rules}, specifying how agents are supposed to add local changes to the information received through their connections~\cite{lamb:memenet}.
 
@@
 The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings.
-For instance, the authors analysis has shown that users tend to copy not the most complete solutions, but instead the first solutions on the graphic interface.
-Additionally, we know from that same paper that users rarely copy solutions from more than 6 neighbours.
+For instance, the authors analysis has shown that users tend to copy not the most complete solutions, but, instead, the first solutions on the graphic interface.
+Additionally, we know from this same paper that users rarely copy solutions from more than 6 neighbours.
 In order to analyse and compare this behaviours, we developed a collection of aggregation rules, each modelling a copying strategy.
@@
 
-We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent to compose a simulated graphic interface in which each agent visualizes some neighbours before or after others.
-Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ solution with probability $X(k)$.
+We inserted this behaviour into our model by firstly generating a random ordering of neighbours for each agent in order to compose a simulated graphic interface.
+As a result, each agent visualizes some neighbours before or after others.
+Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ with probability $X(k)$.
 
@@
 These strategies intend to, given a sudoku puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}".
-We reproduced a variety of these strategies, modelling each one of them as a function mapping a sudoku partial solution to a set of movements.
+We reproduced a variety of these strategies, modelling each one of them as a function that maps a sudoku partial solution to a set of movements.
 
@@
 
-This technique proceeds to mark a sudoku cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.
+This technique marks a sudoku cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.
 For instance, the {\em only choice} rule would mark cell $(1,2)$ with value $4$ in the below sudoku puzzle:
@@
 The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block.
-For instance, the {\em single possibility} rule would mark cell $(4,1)$ with value $7$ in the below sudoku puzzle, since the values $1$,$2$,$3$,$4$,$5$ and $8$ were already present in the cell's column (leaving the possibilities $6$,$7$ and $9$) and the values $6$ and $9$ were already present in the cells' row (leaving the single possibility $7$).
+For instance, the {\em single possibility} rule would mark cell $(4,1)$ with value $7$ in the below sudoku puzzle, since the values $1$, $2$, $3$, $4$, $5$ and $8$ were already present in the cell's column (leaving the possibilities $6$, $7$ and $9$).
+Additionally, the values $6$ and $9$ were already present in the cells' row, thus leaving the single possibility $7$.
 
@@
 
-This rule works on a group of three contiguous $3 \times 3$ blocks.
+This rule applies to groups of three contiguous $3 \times 3$ blocks.
 It aims to find a value $v$ such that $v$ is present in two of the three $3 \times 3$ blocks encompassed by the group, but missing on the third.
-It then proceeds by enumerating all the candidate cells (namely the empty cells) on this block, and then eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks.
+It proceeds by enumerating all the candidate cells - namely the empty cells - on this block, and then, by eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks.
 If the resulting set has cardinality $1$, the rule has successfully found one cell to mark.
-For instance, the {\em two out of three} rule would mark cell $(2,9)$ with value $1$.
+For instance, the {\em two out of three} rule would mark cell $(2,9)$ with value $1$ on the below sudoku.
 

### 2013-01-07 Article.tex
Tornei a seção das regras de apropriação mais enxuta e adicionei a regra "hidden singles"

@@
 
-In sudoku strategy literature, as in chess, we find multiple techniques with iconic names.
+In sudoku strategy literature, as in chess, we find multiple techniques with iconic names~\cite{davis:mathsudoku}.
 Some popular examples are {\em naked singles}, {\em naked twins}, {\em swordfish}.
@@
 This technique marks a sudoku cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.
-For instance, the {\em only choice} rule would mark cell $(1,2)$ with value $4$ in the below sudoku puzzle:
 
-\[ \left( \begin{array}{ccccccccc}
-  &   &   & 7 &   &   &   & 5 & 8 \\
-  & 5 & 6 & 2 & 1 & 8 & 7 & 9 & 3 \\
-  &   &   &   &   &   & 1 &   &   \\
-  &   &   &   &   &   &   & 8 & 1 \\
-  &   &   & 3 & 7 & 6 &   &   &   \\
-9 & 6 &   &   &   &   &   &   &   \\
-  &   & 5 &   &   &   &   &   &   \\
-  &   & 4 &   & 2 & 1 & 8 & 3 &   \\
-8 & 7 &   &   &   & 3 &   &   &   \end{array}  \right)\]
-
-\[ \left( \begin{array}{ccccccccc}
-  &   &   & 7 &   &   &   & 5 & 8 \\
-{\bf 4} & 5 & 6 & 2 & 1 & 8 & 7 & 9 & 3 \\
-  &   &   &   &   &   & 1 &   &   \\
-  &   &   &   &   &   &   & 8 & 1 \\
-  &   &   & 3 & 7 & 6 &   &   &   \\
-9 & 6 &   &   &   &   &   &   &   \\
-  &   & 5 &   &   &   &   &   &   \\
-  &   & 4 &   & 2 & 1 & 8 & 3 &   \\
-8 & 7 &   &   &   & 3 &   &   &   \end{array}  \right)\]
-
-\subsubsection{Single Possibility}
+\subsubsection{Naked Singles}
 
@@
 The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block.
-For instance, the {\em single possibility} rule would mark cell $(4,1)$ with value $7$ in the below sudoku puzzle, since the values $1$, $2$, $3$, $4$, $5$ and $8$ were already present in the cell's column (leaving the possibilities $6$, $7$ and $9$).
-Additionally, the values $6$ and $9$ were already present in the cells' row, thus leaving the single possibility $7$.
 
-\[ \left( \begin{array}{ccccccccc}
-8 & 2 & 5 & 6 & 3 & 1 & 9 & 7 & 4 \\
-  & 6 & 7 &   & 2 & 4 &   &   & 8 \\
-4 &   &   &   &   & 7 & 6 &   & 2 \\
-  & 5 & 9 &   & 4 & 8 & 2 & 6 & 1 \\
-1 &   & 8 & 2 & 6 & 9 & 7 & 4 & 5 \\
-  & 4 &   & 1 & 7 & 5 &   & 8 &   \\
-3 &   & 1 & 4 &   &   &   &   &   \\
-5 &   &   &   &   & 3 & 4 &   &   \\
-2 & 9 & 4 &   &   & 6 & 5 &   &   \end{array}  \right)\]
+\subsubsection{Hidden Singles}
 
-\[ \left( \begin{array}{ccccccccc}
-8 & 2 & 5 & 6 & 3 & 1 & 9 & 7 & 4 \\
-  & 6 & 7 &   & 2 & 4 &   &   & 8 \\
-4 &   &   &   &   & 7 & 6 &   & 2 \\
-{\bf 7} & 5 & 9 &   & 4 & 8 & 2 & 6 & 1 \\
-1 &   & 8 & 2 & 6 & 9 & 7 & 4 & 5 \\
-  & 4 &   & 1 & 7 & 5 &   & 8 &   \\
-3 &   & 1 & 4 &   &   &   &   &   \\
-5 &   &   &   &   & 3 & 4 &   &   \\
-2 & 9 & 4 &   &   & 6 & 5 &   &   \end{array}  \right)\]
+This rule is similar to the {\em naked singles} rule.
+It is able to mark cells with more than one candidate value by looking for cells that are the only cells in their row, column or $3 \times 3$ block that can hold a particular value.
 
@@
 If the resulting set has cardinality $1$, the rule has successfully found one cell to mark.
-For instance, the {\em two out of three} rule would mark cell $(2,9)$ with value $1$ on the below sudoku.
-
-\[ \left( \begin{array}{ccccccccc}
-  &   & 9 & 5 & 1 &   &   & 6 & 2 \\
-6 & 3 & 4 &   &   &   & 5 & 9 &   \\
-1 & 2 & 5 & 6 & 3 & 9 & 7 &   & 4 \\
-2 & 5 &   & 8 & 4 & 7 & 6 & 3 &   \\
-4 & 6 &   &   & 5 &   &   & 1 & 7 \\
-  & 8 & 7 & 3 & 6 & 1 &   & 2 & 5 \\
-5 &   & 6 & 1 & 7 & 3 & 2 & 4 & 8 \\
-  & 1 & 2 &   &   &   & 9 & 7 & 6 \\
-7 & 4 &   &   & 9 & 6 & 1 &   &   \end{array}  \right)\]
-
-\[ \left( \begin{array}{ccccccccc}
-  &   & 9 & 5 & 1 &   &   & 6 & 2 \\
-6 & 3 & 4 &   &   &   & 5 & 9 & {\bf 1} \\
-1 & 2 & 5 & 6 & 3 & 9 & 7 &   & 4 \\
-2 & 5 &   & 8 & 4 & 7 & 6 & 3 &   \\
-4 & 6 &   &   & 5 &   &   & 1 & 7 \\
-  & 8 & 7 & 3 & 6 & 1 &   & 2 & 5 \\
-5 &   & 6 & 1 & 7 & 3 & 2 & 4 & 8 \\
-  & 1 & 2 &   &   &   & 9 & 7 & 6 \\
-7 & 4 &   &   & 9 & 6 & 1 &   &   \end{array}  \right)\]
 

### 2013-01-07 Article.tex
Corrigi algumas coisas no meu texto e consegui adicionar um pouco da notação que tava faltando

@@
 
-We developed a system in which the environment of the sudoku problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
+We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
 The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, providing a basis for the dynamics of the agent network.
@@
 Our solution adapts the {\em Memetic Newtork} technique - originally intended for use in optimization problems - to the context of constraint satisfaction problems.
-In this specific case (sudoku solving), we treat problems with one unique solution.
+In this specific case ({\em Sudoku} solving), we treat problems with one unique solution.
 To deal with this scenario, we propose a {\em Memetic Network} variation in which each agent encodes not a complete, but a partial solution to the problem.
@@
 Our solution employs a fixed topology for the agent network and models cooperation through a set of {\em aggregation rules} and reasoning through a set of {\em appropriation rules}.
-Our aggregation rules specify how sudoku partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with sudoku solving techniques such as naked singles, swordfish, etc.
+Our aggregation rules specify how {\em Sudoku} partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with {\em Sudoku} solving techniques such as naked singles, swordfish, etc.
 
@@
 
-This rule employs the intuitive strategy of copying from the neighbour with the most filled sudoku, namely the most complete solution.
+This rule employs the intuitive strategy of copying from the neighbour with the most filled {\em Sudoku} board, namely the most complete solution.
 
@@
 We know that users tend to copy the first (from left to right) solutions on the graphic interface~\cite{farenzena:collabem}.
-The authors have provided us with a mathematical model of this behaviour, stated as $X(k) = (1-p)^{k-1}p$, where the parameter $p$ is fixed as $p = 0.5479$ and $X(k)$ denotes the probability of an agent copying the $k_{th}$ neighbour solution.
+The authors have provided us with a mathematical model of this behaviour, stated as $\langle X(k)\rangle = (1-p)^{k-1}p$, where the parameter $p$ is fixed as $p = 0.5479$ and $\langle X(k)\rangle$ denotes the probability of an agent copying the $k_{th}$ neighbour solution.
 
@@
 
-In sudoku strategy literature, as in chess, we find multiple techniques with iconic names~\cite{davis:mathsudoku}.
-Some popular examples are {\em naked singles}, {\em naked twins}, {\em swordfish}.
-These strategies intend to, given a sudoku puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}".
-We reproduced a variety of these strategies, modelling each one of them as a function that maps a sudoku partial solution to a set of movements.
+In {\em Sudoku} strategy literature, as in chess, we find multiple techniques with iconic names.
+Some popular examples are the {\em naked singles} rule, the {\em naked twins} rule and the {\em swordfish} rule, studied in ~\cite{davis:mathsudoku}.
+These strategies intend to, given a {\em Sudoku} puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}".
+We reproduced a variety of these strategies, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of movements.
 
@@
 
-This technique marks a sudoku cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.
+This technique marks a {\em Sudoku} cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.
 
@@
 
-This rule marks a sudoku cell with value $v$ only if $v$ is the single possible value to mark that cell.
+This rule marks a {\em Sudoku} cell with value $v$ only if $v$ is the single possible value to mark that cell.
 The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block.

### 2013-01-07 Article.tex
Expandi um pouco a introdução, ainda vou refinar ela

@@
 For years multi-agent systems have been used to research cooperation as a tool for problem-solving.
-Recently, however, there has been an increasing interest in the use of human beings as problem-solving agents.
-Several studies have been conducted in which subjects are connected in a network with the goal of searching for the solution of a specific problem, and those have helped shed some light on the way humans interact in order to solve problems.
+Recently, however, there has been an increasing interest in the study of human beings as problem-solving agents.
+Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems.
+However, those studies are limited to obtaining observations on human behaviour and formulating hypotheses, being unable to explain with certainty that behaviour.
+In this paper, we use a multi-agent based simulation to complement the study of human computation, as a way of explaining the strategies used by humans and understanding their consequences in a cooperative environment.
+
+Human beings are known to be able to easily perform tasks which are still generally difficult for computers, such as natural language processing and image recognition.
+However, it would be useful to be able to apply human computation to more classical computer problems with precise definitions and algorithms, but which are still computationally intensive.
+The different sets of abilities between computers and humans suggest that human computation might provide a new approach to those problems, one that computers can't easily apply.
+However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional techniques.
+To take full advantage of human problem-solving skills, we must learn their limitations.
+In order to obtain that knowledge, we have developed a multi-agent system that simulates human behaviour according to findings of experiments performed in humans.
+
+\section{Background}
 
@@
 
-Another result of those observations is that there is a higher probability of individuals copying peers' solutions when those are shared by several neighbours, referred to as an evidence of \emph{conformist behaviour}.
+Another result of those observations is that there is a higher probability of individuals copying peers' solutions when those are shared by several neighbours, referred to by the authors as \emph{conformist behaviour}.
 A similar behaviour was observed in \cite{mason:collablearnet} for a different problem.
-
-We have built a multi-agent system that simulates the experiments of \cite{farenzena:collabem} with the aim of verifying whether the strategies employed by humans are competitive with other heuristics.
-After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.
-
-\section{Background}
-
-Background
 
@@
 
-Contribution
+We have built a multi-agent system that simulates the experiments of \cite{farenzena:collabem}, using the model of human behaviour proposed by them.
+We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by \cite{lamb:memenet}.
+For simplicity, we limited our experiments to the Sudoku problem.
+Our goal is verifying whether the strategies employed by humans are competitive with other heuristics.
+After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.
 

### 2013-01-09 Article.tex
"refatorei" o texto

@@
 Our solution employs a fixed topology for the agent network and models cooperation through a set of {\em aggregation rules} and reasoning through a set of {\em appropriation rules}.
-Our aggregation rules specify how {\em Sudoku} partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with {\em Sudoku} solving techniques such as naked singles, swordfish, etc.
+Our aggregation rules specify how {\em Sudoku} partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with {\em Sudoku} solving techniques such as those studied in~\cite{davis:mathsudoku}.
 
@@
 In {\em Sudoku} strategy literature, as in chess, we find multiple techniques with iconic names.
-Some popular examples are the {\em naked singles} rule, the {\em naked twins} rule and the {\em swordfish} rule, studied in ~\cite{davis:mathsudoku}.
-These strategies intend to, given a {\em Sudoku} puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as "{\em mark cell 1 of column 3 with value 5}".
+Some popular examples are the {\em naked singles} rule, the {\em hidden singles} rule and the {\em naked twins} rule, studied in ~\cite{davis:mathsudoku}.
+These strategies intend to, given a {\em Sudoku} puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as {\em "mark cell 1 of column 3 with value 5"}.
 We reproduced a variety of these strategies, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of movements.

### 2013-01-09 Article.tex
Commit não deu certo, tive que refazer

@@
 Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems.
-However, those studies are limited to obtaining observations on human behaviour and formulating hypotheses, being unable to explain with certainty that behaviour.
+However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed behaviour.
 In this paper, we use a multi-agent based simulation to complement the study of human computation, as a way of explaining the strategies used by humans and understanding their consequences in a cooperative environment.
+The control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the ones displayed by humans.
 
 Human beings are known to be able to easily perform tasks which are still generally difficult for computers, such as natural language processing and image recognition.
-However, it would be useful to be able to apply human computation to more classical computer problems with precise definitions and algorithms, but which are still computationally intensive.
-The different sets of abilities between computers and humans suggest that human computation might provide a new approach to those problems, one that computers can't easily apply.
+However, it would be useful to be able to apply human social computation to more straightforward computer problems with precise definitions and algorithms, but which are still computationally intensive.
+The different sets of abilities between computers and humans suggest that the latter might provide a new approach to those problems that might be more effective than current techniques employed by computers.
+That notion has been successfully applied, for example, in one of the most significant problems in the field of bioinformatics: protein structure prediction (PSP).
+A software that presents the problem to humans as an online computer game, called \emph{Foldit} \cite{cooper:foldit}, has produced significant results in the research of PSP, which is usually approached as an optimization problem requiring extensive computational power.
+Those results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration \cite{cooper:foldit}.
 However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional techniques.
-To take full advantage of human problem-solving skills, we must learn their limitations.
-In order to obtain that knowledge, we have developed a multi-agent system that simulates human behaviour according to findings of experiments performed in humans.
+To take full advantage of human problem-solving strategies, we must learn their limitations.
+In order to obtain that knowledge, our system simulates human behaviour according to findings of social computation experiments.
 
@@
 
+Social computation is a relatively new area of research with a diversified, interdisciplinary root that mixes social sciences, artificial intelligence, game theory and network science, among others.
+Only recently studies on the potential of human social networks for solving problems are gaining some popularity.
+Those have provided insights into, among other things, the impact of network structure in the collaboration process and the factors that lead neighbours' proposed solutions to be copied by individuals.
+
+The origin of human computation as we know it today can be traced back to the work of \cite{vonahm:gwap}, which identified the possibility of using entertainment as an incentive to participation of human subjects, applying it in games in which the participants are actually performing a computation.
+That is an idea that also appears in the Foldit game.
+
+The series of experiments summarized in \cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems.
+The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal.
+
+Other initiatives have appeared, such as the ones by \cite{farenzena:collabem} and \cite{mason:collablearnet}, which take a different approach by having subjects trying to solve the collective problem individually, with the possibility of exchanging solutions between neighbours.
+Those have resulted in interesting conclusions on human behaviour when the possibility of copying peers makes itself present.
+It's in those models of experiments that we will focus in this work.
+
 The experiments conducted by \cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question.
-The behaviour observed in that study has provided evidence that human beings in a cooperative problem-solving environment might not evaluate solutions proposed by their peers, instead choosing the most readily available one.
+There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:
 
-Another result of those observations is that there is a higher probability of individuals copying peers' solutions when those are shared by several neighbours, referred to by the authors as \emph{conformist behaviour}.
-A similar behaviour was observed in \cite{mason:collablearnet} for a different problem.
+\begin{itemize}
+	\item Humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one.
+On the other hand, \cite{mason:collablearnet} suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that wasn't provided.
+	\item There is a higher probability of individuals copying peers' solutions when those are shared by several neighbours.
+That behaviour is referred to by the authors as \emph{conformism}.
+A similar behaviour was observed by \cite{mason:collablearnet}, even though the experiments used a different problem.
+\end{itemize}
+
+\cite{mason:collablearnet} also provided important insights to human cooperation.
+However, since our basis is the work of \cite{farenzena:collabem} we will use the former's results only as secondary support.
 

### 2013-01-10 Article.tex
commit

@@
-%%%% ijcai11.tex
+%\documentclass{article}
+%\usepackage{ijcai13}
+%\usepackage{times}
+%\usepackage{latexsym}
 
-\typeout{IJCAI-13 Instructions for Authors}
+\documentclass[letterpaper]{article}
+\usepackage{aaai}
+\usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
+\frenchspacing
 
-% These are the instructions for authors for IJCAI-13.
-% They are the same as the ones for IJCAI-11 with superficical wording
-%   changes only.
-
-\documentclass{article}
-% The file ijcai13.sty is the style file for IJCAI-13 (same as ijcai07.sty).
-\usepackage{ijcai13}
-
-% Use the postscript times font!
-\usepackage{times}
-
-\usepackage{latexsym}
+\usepackage{graphicx}
 
 \title{Social Computing Article\thanks{This title is temporary}}
-\author{Tabajara, Lucas \\
-Institute of Informatics \\
-Federal University of Rio Grande do Sul\\
-Brazil \\
-lmtabajara@inf.ufrgs.br
-\and
-Prates, Marcelo \\
-Institute of Informatics \\
-Federal University of Rio Grande do Sul\\
-Brazil \\
-morprates@inf.ufrgs.br}
 
@@
 As a result, each agent visualizes some neighbours before or after others.
-Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ with probability $X(k)$.
+Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.
 
@@
 This rule is similar to the {\em naked singles} rule.
-It is able to mark cells with more than one candidate value by looking for cells that are the only cells in their row, column or $3 \times 3$ block that can hold a particular value.
+It is able to mark cells with more than one candidate value by looking for cells that are the only ones in their row, column or $3 \times 3$ block that can hold a particular value.
 
@@
 It proceeds by enumerating all the candidate cells - namely the empty cells - on this block, and then, by eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks.
-If the resulting set has cardinality $1$, the rule has successfully found one cell to mark.
+If the resulting set has cardinality $1$, the rule has successfully found a cell to mark.
 
 \subsubsection{Naked Twins}
+
+\subsection{Copying Solutions}
+
+In a study conducted by~\cite{farenzena:collabem}, subjects were invited to solve {\em Sudoku} puzzles and share them with other subjects with whom they were connected through a network topology.
+At any time, a player could copy solutions from one of his or her neighbours.
+The authors' analysis has shown that there is a different copy frequency associated with each topology.
+For instance, the scale free topology with $\gamma = 1.65$ resulted in a copy frequency of $87 \%$, while the fully connected topology resulted in a copy frequency of $42 \%$.
+
+We incorporated this copying frequency into our modelling, recreating the scenario of the experiments conducted by~\cite{farenzena:collabem} by setting this parameter accordingly to the topologies we used.
+
+\subsection{Conformist Behaviour}
+
+We introduce in our modelling the {\em conformist} behaviour proposed by~\cite{cefferson:conformists} and further studied by~\cite{farenzena:collabem}, which states that agents tend to copy a particular solution with probability $1$ when surrounded by neighbours that share this solution.
+
+Our approach was to establish a {\em treshold} determining a minimum necessary quantity $N$ of neighbours sharing a particular solution.
+In our modelling, all agents with $N$ or more neighbours having a solution $s$ in common are programmed to copy solution $s$ from them.
+
+\subsection{Guessing and Backtracking}
+
+We have consistent evidence that trial-and-error is a part of the {\em Sudoku} solving experience.
+The need for trial-and-error in {\em Sudoku} puzzles is not a falsifiable conclusion, but a mathematical fact~\cite{davis:mathsudoku}.
+Some puzzles are only solvable by the means of a backtracking procedure (see Figure 1).
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.30]{trial_and_error_sudoku}
+\caption{A {\em Sudoku} puzzle solvable only by trial-and-error}
+\label{fig:trial_and_error_sudoku}
+\end{figure}
+
+In our modelling, we associate each agent with a numerical parameter determining the probability of this agent to guess when incapable of applying a typical {\em Sudoku} solving strategy.
+
+Automatic {\em Sudoku} solvers employing a backtracking algorithm are easily programmed and very time-efficient.
+On the other hand, the space complexity of these algorithms is a barrier to most human solvers, who need to write down tons of observations in order to employ a backtracking strategy.
+With this in mind, we propose in our modelling two different kinds of backtracking, intended to be more similar to the way human beings employ error correction in {\em Sudoku} solving in a collaborative environment such as the one analysed in~\cite{farenzena:collabem}.
+
+\begin{itemize}
+
+\item
+Local Backtracking: When faced with one or more conflicts in its own solution, an agent simply erases the conflicting cells.
+\item
+Social Backtracking: When faced with one or more conflicts in its own solution, an agent copies a solution from one of its neighbours.
+In our modelling, this is done by raising the copy rate of this particular agent to $1$.
+
+\end{itemize}
 
@@
 
+\section{Acknowledgements}
+
+Research partly supported by CPNPq and CAPES, Brazil.
+
 %% The file named.bst is a bibliography style file for BibTeX 0.99c

### 2013-01-11 Article.tex
Atualizei o artigo substituindo a nomenclatura do nosso método

@@
 \usepackage{courier}
+\usepackage{algorithm2e}
 \frenchspacing
@@
 
-\section{Sudoku Solving Memetic Network}
+\section{A Novel Method for Agent-based Social Problem Solving}
 
-A {\em Memetic Network Algorithm} is composed of an ordered set of $N$ agents, each encoding a complete solution to the optimization problem, and a binary $N \times N$ matrix representing possible connections between agents.
-Additionally, a {\em Memetic Network Algorithm} is composed of a set of rules specifying how connections between agents are formed and erased and how interactions between these agents take place.
-These rules are grouped under the categories of {\em Connection Rules}, specifying how agents will connect and disconnect from each other; {\em Aggregation Rules}, specifying the dynamics of the information flow through connections; and {\em Appropriation Rules}, specifying how agents are supposed to add local changes to the information received through their connections~\cite{lamb:memenet}.
+A number of multi-agent methodologies that employ information flow through agents have been studied before.
+For instance, the {\em Memetic Networks} model proposed by~\cite{lamb:memenet} draws inspiration from the phenomenon of {\em Cultural Evolution} discussed by Dawkins in~\cite{dawkins:selfishgene} and has a network of agents sharing, copying and incrementing units of information in a similar way that nature, according to Dawkins, deals with {\em Memes}~\cite{dawkins:selfishgene}.
+Nevertheless, some aspects of social behaviour of great significance to social computing cannot be properly analysed through this methodologies.
+One example is the conformist behaviour studied in~\cite{cefferson:conformists} and~\cite{farenzena:collabem}.
+The proper study of these aspects demands a novel method for agent-based collaborative problem solving.
 
-Our solution adapts the {\em Memetic Newtork} technique - originally intended for use in optimization problems - to the context of constraint satisfaction problems.
-In this specific case ({\em Sudoku} solving), we treat problems with one unique solution.
-To deal with this scenario, we propose a {\em Memetic Network} variation in which each agent encodes not a complete, but a partial solution to the problem.
+We propose a method for solving computational problems by the means of a network of agents with social behaviour.
+Our algorithm is composed of an ordered set of $N$ agents, each encoding a partial solution to the problem, and a binary $N \times N$ matrix representing possible connections between agents.
+Additionally, our algorithm is composed of two stages, namely the {\em Social Stage} and the {\em Cognitive Stage}.
 
-Our solution employs a fixed topology for the agent network and models cooperation through a set of {\em aggregation rules} and reasoning through a set of {\em appropriation rules}.
-Our aggregation rules specify how {\em Sudoku} partial solutions are copied from agent to agent, while our appropriation rules specify how agents increment these solutions with {\em Sudoku} solving techniques such as those studied in~\cite{davis:mathsudoku}.
+\begin{itemize}
+\item
+Social Stage: In the {\em Social Stage}, messages are passed from agent to agent through the network connections.
+Agents are thus presented with a multiplicity of messages.
+There is a particular probability associated with the agents choosing to copy one of these solutions in contrast to keeping their current solutions.
+We call this probability the {\em Copy Rate}.
+When an agent chooses to copy, he or she is then supposed to select for copying only one of his or her received messages.
+This is done by the means of a particular message-selecting metric.
 
-\subsection{Aggregation Rules}
+\item
+Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by the means of a heuristic or an exact method.
+\end{itemize}
+
+\begin{algorithm}
+ \SetAlgoLined
+ Initialize N agents, each encoding a partial solution to the problem\;
+ \While{termination condition not met}
+ {
+ 	\For{i = 1 to N}
+ 	{
+ 		\For{j = 1 to N}
+ 		{
+ 			\If{j is connected to i}
+ 			{
+ 				A = $i_{th}$ agent\;
+ 				A.messages.add(j.solution)\;
+ 			}
+ 		}
+ 	}
+ 	\For{i = 1 to N} 
+ 	{
+ 		\CommentSty{ //Social Stage }\;
+ 		A = $i_{th}$ agent\;
+ 		selectedMessage = select(A.messages)\;
+
+ 		\If{random(0,1) $<$ copyRate}
+ 		{
+ 			A.solution = selectedMessage\;
+ 		}
+ 	}
+ 	\For{i = 1 to N}
+ 	{
+ 		\CommentSty{ //Cognitive Stage }\;
+ 		A = $i_{th}$ agent\;
+ 		A.solution = addLocalChanges(A.solution)\;
+ 	}
+ }
+ \caption{No name yet}
+\end{algorithm}
+
+\section{Performance Tests}
+
+In order to validate the algorithm as a social problem solving technique, we have modelled the collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through it and tested it over a set of {\em Sudoku} instances.
+
+\subsection{Social Stage}
 
 The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings.
-For instance, the authors analysis has shown that users tend to copy not the most complete solutions, but, instead, the first solutions on the graphic interface.
-Additionally, we know from this same paper that users rarely copy solutions from more than 6 neighbours.
-In order to analyse and compare this behaviours, we developed a collection of aggregation rules, each modelling a copying strategy.
+For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of copying the most complete solutions.
+In order to analyse and compare this two behaviours, he have modelled each one of them as a message-selecting metric for the {\em Social Stage}.
 
-\subsubsection{Pick Most Filled}
+\subsubsection{{\em Pick Most Filled} metric}
 
-This rule employs the intuitive strategy of copying from the neighbour with the most filled {\em Sudoku} board, namely the most complete solution.
+This metric employs the intuitive strategy of selecting the most complete message for copying.
+In the specific case of {\em Sudoku} solving, this metric selects the most filled {\em Sudoku} partial solution.
+Put in other words, it selects the {\em Sudoku} partial solution with the lesser number of blank cells.
 
-\subsubsection{Pick Among First}
+\subsubsection{{\em Pick Among First} metric}
 
-We know that users tend to copy the first (from left to right) solutions on the graphic interface~\cite{farenzena:collabem}.
+We know that, in some settings of collaborative problem-solving, human subjects are likely to copy the first (from left to right) solutions on the graphic interface~\cite{farenzena:collabem}.
 The authors have provided us with a mathematical model of this behaviour, stated as $\langle X(k)\rangle = (1-p)^{k-1}p$, where the parameter $p$ is fixed as $p = 0.5479$ and $\langle X(k)\rangle$ denotes the probability of an agent copying the $k_{th}$ neighbour solution.
@@
 As a result, each agent visualizes some neighbours before or after others.
-Secondly, we translated the above mathematical model into an aggregation rule in which the solution copied by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.
+Secondly, we translated the above mathematical model into an message-selecting metric in which the solution selected by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.
 
-\subsection{Appropriation Rules}
+\subsection{Cognitive Stage}
 
-In {\em Sudoku} strategy literature, as in chess, we find multiple techniques with iconic names.
-Some popular examples are the {\em naked singles} rule, the {\em hidden singles} rule and the {\em naked twins} rule, studied in ~\cite{davis:mathsudoku}.
-These strategies intend to, given a {\em Sudoku} puzzle in a partial state of completion, generate movements to mark blank cells of the puzzle, as {\em "mark cell 1 of column 3 with value 5"}.
-We reproduced a variety of these strategies, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of movements.
+{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature.~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples.
+These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} with can be used to mark cells of this {\em Sudoku} puzzle.
+We implemented $4$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}.
+These functions can be used in the {\em Cognitive Stage} to add local changes to the {\em Sudoku} message received in the {\em Social Stage}.
 
@@
 
-We introduce in our modelling the {\em conformist} behaviour proposed by~\cite{cefferson:conformists} and further studied by~\cite{farenzena:collabem}, which states that agents tend to copy a particular solution with probability $1$ when surrounded by neighbours that share this solution.
+We introduce in our modelling the {\em conformist} behaviour proposed by~\cite{cefferson:conformists} and further studied by~\cite{farenzena:collabem}, which states that agents are likely to copy a particular solution with probability $1$ when surrounded by neighbours that share this solution.
 
@@
 
-Research partly supported by CPNPq and CAPES, Brazil.
+We are grateful to Diego Noble and Cristiano *{\em qual sobrenome?}* for their advice, contribution and proofreading. Research partly supported by CPNPq and CAPES, Brazil.
 

### 2013-01-11 Article.tex
corrigi coisinhas na bibliografia e etc

@@
 We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
-The optimization technique of {\em Memetic Networks}~\cite{lamb:memenet} was employed on the modelling, providing a basis for the dynamics of the agent network.
+We conceived a novel method for agent-based social problem solving witch draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{lamb:memenet}.
 
@@
 Agents are thus presented with a multiplicity of messages.
-There is a particular probability associated with the agents choosing to copy one of these solutions in contrast to keeping their current solutions.
+There is a particular probability associated with the behaviour of agents choosing to copy one of these solutions in contrast to keeping their current solutions.
 We call this probability the {\em Copy Rate}.
@@
 
-{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature.~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples.
-These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} with can be used to mark cells of this {\em Sudoku} puzzle.
+{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature.Davis ~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples.
+These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle.
 We implemented $4$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}.

### 2013-01-14 Article.tex
Adicionei um esboço da seção de resultados e ajeitei umas outras coisas

@@
 We have built a multi-agent system that simulates the experiments of \cite{farenzena:collabem}, using the model of human behaviour proposed by them.
-We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by \cite{lamb:memenet}.
+We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by \cite{araujo:memenet}.
 For simplicity, we limited our experiments to the Sudoku problem.
@@
 We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
-We conceived a novel method for agent-based social problem solving witch draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{lamb:memenet}.
+We conceived a novel method for agent-based social problem solving witch draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.
 
@@
 A number of multi-agent methodologies that employ information flow through agents have been studied before.
-For instance, the {\em Memetic Networks} model proposed by~\cite{lamb:memenet} draws inspiration from the phenomenon of {\em Cultural Evolution} discussed by Dawkins in~\cite{dawkins:selfishgene} and has a network of agents sharing, copying and incrementing units of information in a similar way that nature, according to Dawkins, deals with {\em Memes}~\cite{dawkins:selfishgene}.
+For instance, the {\em Memetic Networks} model proposed by~\cite{araujo:memenet} draws inspiration from the phenomenon of {\em Cultural Evolution} discussed by Dawkins in~\cite{dawkins:selfishgene} and has a network of agents sharing, copying and incrementing units of information in a similar way that nature, according to Dawkins, deals with {\em Memes}~\cite{dawkins:selfishgene}.
 Nevertheless, some aspects of social behaviour of great significance to social computing cannot be properly analysed through this methodologies.
@@
 
-{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature.Davis ~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples.
+{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature.
+Davis ~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples.
 These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle.
-We implemented $4$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}.
+We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}.
 These functions can be used in the {\em Cognitive Stage} to add local changes to the {\em Sudoku} message received in the {\em Social Stage}.
 
-\subsubsection{Only Choice}
+The rules implemented were the {\em Unique Missing Candidate} rule, the {\em Naked Singles} rule, the {\em Hidden Singles} rule, the {\em Two out of Three} rule and the {\em Naked Twins} rule, all of which (with the exception of the {\em Two out of Three} rule) are discussed in~\cite{davis:mathsudoku}.
+In our modelling, each agent knows a particular quantity of rules, this quantity determining the agent's {\em level}.
+Our tests were all conducted with a heterogeneous population of agents of different {\em levels}.
+We detail below each one of the implemented rules.
+
+\subsubsection{Unique Missing Candidate}
 
@@
 
-\section{Results}
+\section{Results and Analysis}
 
-Results
+We tested the above modelling using an heterogeneous, uniform agent distribution in which every agent {\em level} ($0$ to $5$) had an equal representation in the population.
+We performed tests with varying values for the parameters of {\em copy rate}, {\em guess rate}, {\em message selecting metric} and {\em network topology}.
+
+\subsection{Copying and Guessing are beneficial to the Algorithm's Performance}
+
+~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}.
+Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure 2 and Figure 3).
+The graphs in Figure 2 and Figure 3 - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a peak in ({\em copy rate}: 7, {\em guess rate}: 0) and a valley in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
+We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells.
+These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.60]{copy_guess_free_most}
+\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric)
+}
+\label{fig:copy_guess_free_most}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.60]{copy_guess_free_prob}
+\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick among first' selection metric)
+}
+\label{fig:copy_guess_free_most}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.60]{copy_guess_free_prob_num_solution_reached}
+\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick among first' selection metric)
+}
+\label{fig:copy_guess_free_prob_num_solution_reached}
+\end{figure}
 
@@
 Conclusions
-
-\section{Acknowledgements}
-
-We are grateful to Diego Noble and Cristiano *{\em qual sobrenome?}* for their advice, contribution and proofreading. Research partly supported by CPNPq and CAPES, Brazil.
 

### 2013-01-14 Article.tex
Escrevi um pouco nos resultados

@@
 That notion has been successfully applied, for example, in one of the most significant problems in the field of bioinformatics: protein structure prediction (PSP).
-A software that presents the problem to humans as an online computer game, called \emph{Foldit} \cite{cooper:foldit}, has produced significant results in the research of PSP, which is usually approached as an optimization problem requiring extensive computational power.
-Those results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration \cite{cooper:foldit}.
+A software that presents the problem to humans as an online computer game, called \emph{Foldit}~\cite{cooper:foldit}, has produced significant results in the research of PSP, which is usually approached as an optimization problem requiring extensive computational power.
+Those results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration~\cite{cooper:foldit}.
 However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional techniques.
@@
 
-The origin of human computation as we know it today can be traced back to the work of \cite{vonahm:gwap}, which identified the possibility of using entertainment as an incentive to participation of human subjects, applying it in games in which the participants are actually performing a computation.
+The origin of human computation as we know it today can be traced back to the work of~\cite{vonahm:gwap}, which identified the possibility of using entertainment as an incentive to participation of human subjects, applying it in games in which the participants are actually performing a computation.
 That is an idea that also appears in the Foldit game.
 
-The series of experiments summarized in \cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems.
+The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems.
 The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal.
 
-Other initiatives have appeared, such as the ones by \cite{farenzena:collabem} and \cite{mason:collablearnet}, which take a different approach by having subjects trying to solve the collective problem individually, with the possibility of exchanging solutions between neighbours.
+Other initiatives have appeared, such as the ones by~\cite{farenzena:collabem} and~\cite{mason:collablearnet}, which take a different approach by having subjects trying to solve the collective problem individually, with the possibility of exchanging solutions between neighbours.
 Those have resulted in interesting conclusions on human behaviour when the possibility of copying peers makes itself present.
@@
 
-The experiments conducted by \cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question.
+The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question.
 There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:
@@
 	\item Humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one.
-On the other hand, \cite{mason:collablearnet} suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that wasn't provided.
+On the other hand,~\cite{mason:collablearnet} suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that wasn't provided.
 	\item There is a higher probability of individuals copying peers' solutions when those are shared by several neighbours.
 That behaviour is referred to by the authors as \emph{conformism}.
-A similar behaviour was observed by \cite{mason:collablearnet}, even though the experiments used a different problem.
+A similar behaviour was observed by~\cite{mason:collablearnet}, even though the experiments used a different problem.
 \end{itemize}
@@
 \cite{mason:collablearnet} also provided important insights to human cooperation.
-However, since our basis is the work of \cite{farenzena:collabem} we will use the former's results only as secondary support.
+However, since our basis is the work of~\cite{farenzena:collabem} we will use the former's results only as secondary support.
 
@@
 
-We have built a multi-agent system that simulates the experiments of \cite{farenzena:collabem}, using the model of human behaviour proposed by them.
-We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by \cite{araujo:memenet}.
+We have built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
+We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by~\cite{araujo:memenet}.
 For simplicity, we limited our experiments to the Sudoku problem.
@@
 
+\subsection{Evaluating the neighbours' solutions is beneficial}
+
+Of the three metric employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours.
+The other chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly.
+Our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy.
+In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution.
+That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.
+
 \section{Conclusions}

### 2013-01-14 Article.tex
mexi um pouco nos resultados e arrumei algumas coisas ao longo do texto

@@
 
-We have built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
-We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by~\cite{araujo:memenet}.
-For simplicity, we limited our experiments to the Sudoku problem.
+We have developed and detailed a novel method for agent-based social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
+It was used it to built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
+For simplicity, we limited our experiments to the {\em Sudoku} problem.
 Our goal is verifying whether the strategies employed by humans are competitive with other heuristics.
@@
 We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
-We conceived a novel method for agent-based social problem solving witch draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.
+We conceived a novel method for agent-based social problem solving which draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.
 
@@
 
-~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}.
+Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}.
 Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure 2 and Figure 3).
@@
 These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions.
+Also, as shown in Figure 4, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.
 
@@
 
-Of the three metric employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours.
+Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours.
 The other chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly.

### 2013-01-14 Article.tex
Atualizei os headings (acho que tinha que ficar tudo em maísuculo)

@@
 
-\subsection{Copying and Guessing are beneficial to the Algorithm's Performance}
+\subsection{Copying and Guessing are Beneficial to the Algorithm's Performance}
 
@@
 Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure 2 and Figure 3).
-The graphs in Figure 2 and Figure 3 - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a peak in ({\em copy rate}: 7, {\em guess rate}: 0) and a valley in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
+The graphs in Figure 2 and Figure 3 - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
 We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells.
@@
 
-\subsection{Evaluating the neighbours' solutions is beneficial}
+\subsection{Evaluating the Neighbours' Solutions is Beneficial}
 

### 2013-01-15 Article.tex
arrumei umas coisinhas e atualizei os gráficos

@@
 
-\subsubsection{Unique Missing Candidate}
-
-This technique marks a {\em Sudoku} cell with a value only if this cell is the last blank cell on its row, column or $3 \times 3$ block.
-
-\subsubsection{Naked Singles}
-
-This rule marks a {\em Sudoku} cell with value $v$ only if $v$ is the single possible value to mark that cell.
-The other values must have been eliminated through a process of verifying that they are all present in the span encompassing the cell's row, column and $3 \times 3$ block.
-
-\subsubsection{Hidden Singles}
-
-This rule is similar to the {\em naked singles} rule.
-It is able to mark cells with more than one candidate value by looking for cells that are the only ones in their row, column or $3 \times 3$ block that can hold a particular value.
-
-\subsubsection{Two out of Three}
+\subsubsection{Two out of Three Rule}
 
@@
 If the resulting set has cardinality $1$, the rule has successfully found a cell to mark.
-
-\subsubsection{Naked Twins}
 

### 2013-01-15 Article.tex
Escrevi sobre os resultados da most

@@
 Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours.
-The other chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly.
-Our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy.
+Another chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly.
+
+As can be seen in Figure~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy.
 In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution.
 That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.
+
+The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy, and both underperformed in comparison to evaluating the solutions according to number of filled cells.
+This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of problem-solving.
+
+Even so, that behaviour was observed in human networks.
+\cite{farenzena:collabem} has suggested that human beings behave like that because in the real world the environment continuously selects against ineffective solutions, since a bad choice in solving a real world problem might cause and agent to cease communication.
+Since neither the original experiments nor our simulation included such a mechanism, the advantages of that process have not been observed, but they might already be good enough that it may not justify the effort for the agents to evaluate the solutions.
+
+Another explanation might be that humans might find difficult evaluating sudoku partial solutions.
+Although we have used the number of filled cells as a metric, that is not guaranteed to accurately measure which solution is best, since individuals might fill in cells with the wrong value.
+That hypothesis is supported by the experiments of~\cite{mason:collablearnet}, which used optimization of multidimensional functions as the problem being solved.
+This problem has a straightforward and accurate method of determining the fitness of a solution, which is simply the value of the given function for the proposed coordinates.
+In this experiments, the subjects seemingly did effectively evaluate the proposed solutions, giving preference to the ones that were better evaluated.
+The difference in behaviour between the two experiments might be because in the latter the fitness of a certain solution was obvious to the agent, while in the former it's not as easy to pick the best solution out of the available ones.
+
+Knowing that, systems that take advantage of human computation might take advantage of the computer aspect of human computation to encourage selection of better-evaluated solutions.
+One possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead using a pre-specified or random order.
+However, that might introduce a _ in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques.
+To avoid that, perhaps simply displaying the evaluation of each solution might be enough to encourage that behaviour.
+
+\begin{figure}
+\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration}
+\label{fig:progression}
+\end{figure}
 

### 2013-01-16 Article.tex
Criei uma seção especial pras 'guidelines' sobre o design de sistemas de computação social; escrevi um esboço da conclusão; arrumei algumas
coisas e botei a imagem da progressão

@@
  			{
- 				A = $i_{th}$ agent\;
- 				A.messages.add(j.solution)\;
+ 				$A_{i}$ = $i_{th}$ agent\;
+ 				$A_{j}$ = $j_{th}$ agent\;
+ 				Add $A_{j}$'s solution to the collection of messages of $A_{i}$\; %A.messages.add(j.solution)\;
  			}
@@
  		\CommentSty{ //Social Stage }\;
- 		A = $i_{th}$ agent\;
- 		selectedMessage = select(A.messages)\;
+ 		$A_{i}$ = $i_{th}$ agent\;
+ 		selectedMessage = select($A_{i}$.messages)\;
 
@@
  		{
- 			A.solution = selectedMessage\;
+ 			$A_{i}$.solution = selectedMessage\;
  		}
@@
  		\CommentSty{ //Cognitive Stage }\;
- 		A = $i_{th}$ agent\;
- 		A.solution = addLocalChanges(A.solution)\;
+ 		$A_{i}$ = $i_{th}$ agent\;
+ 		Add local changes to $A_{i}$'s solution%$A_{i}$.solution = addLocalChanges($A_{i}$.solution)\;
  	}
@@
 Our tests were all conducted with a heterogeneous population of agents of different {\em levels}.
-We detail below each one of the implemented rules.
+We detail below the 'two out of three' rule.
+For details on the other $4$ rules, see ~\cite{davis:mathsudoku}.
 
@@
 
-We introduce in our modelling the {\em conformist} behaviour proposed by~\cite{cefferson:conformists} and further studied by~\cite{farenzena:collabem}, which states that agents are likely to copy a particular solution with probability $1$ when surrounded by neighbours that share this solution.
+We introduce in our modelling the {\em conformist} behaviour proposed by~\cite{cefferson:conformists} and further studied by~\cite{farenzena:collabem}, which states that agents are likely to copy a particular solution when surrounded by neighbours that share this solution.
 
@@
 The need for trial-and-error in {\em Sudoku} puzzles is not a falsifiable conclusion, but a mathematical fact~\cite{davis:mathsudoku}.
-Some puzzles are only solvable by the means of a backtracking procedure (see Figure 1).
+Some puzzles are only solvable by the means of a backtracking procedure (see Figure~\ref{fig:trial_and_error_sudoku}).
 
 \begin{figure}
-\centering
 \includegraphics[scale=0.30]{trial_and_error_sudoku}
@@
 Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}.
-Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure 2 and Figure 3).
-The graphs in Figure 2 and Figure 3 - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
+Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob}).
+The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
 We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells.
 These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions.
-Also, as shown in Figure 4, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.
+Also, as shown in Figure~\ref{fig:copy_guess_free_prob_num_solution_reached}, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.
 
 \begin{figure}
-\centering
 \includegraphics[scale=0.60]{copy_guess_free_most}
@@
 \begin{figure}
-\centering
 \includegraphics[scale=0.60]{copy_guess_free_prob}
@@
 }
-\label{fig:copy_guess_free_most}
+\label{fig:copy_guess_free_prob}
 \end{figure}
@@
 \begin{figure}
-\centering
 \includegraphics[scale=0.60]{copy_guess_free_prob_num_solution_reached}
@@
 
-\subsection{Evaluating the Neighbours' Solutions is Beneficial}
+\subsection{Evaluating the Neighbours' Solutions is Beneficial to the Algorithm's Performance}
 
@@
 
-As can be seen in Figure~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy.
+As can be seen in Figures ~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy.
 In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution.
@@
 
+\subsection{Small Changes on the Interface Might Improve the Performance of Human Beings in Human Computation Environments}
+
 Knowing that, systems that take advantage of human computation might take advantage of the computer aspect of human computation to encourage selection of better-evaluated solutions.
 One possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead using a pre-specified or random order.
-However, that might introduce a _ in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques.
+However, that might introduce a (BLANK) in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques.
 To avoid that, perhaps simply displaying the evaluation of each solution might be enough to encourage that behaviour.
@@
 \begin{figure}
-\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration}
+\includegraphics[scale=0.50]{progression}
+\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
+}
 \label{fig:progression}
@@
 
-Conclusions
+We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments.
+To do this, we proposed a novel method for agent-based social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}.
+We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems.
+We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes.
+With these results in mind, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.
 

### 2013-01-16 Article.tex
corrigi algumas coisas e adicionei o abstract

@@
 \begin{abstract}
-  Abstract
+Social collaboration has been shown to facilitate problem-solving activity in a diverse set of environments.
+Nevertheless, if not well designed, a social human computation system may achieve results as poor as those of a single human subject performing a task.
+This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks.
+We present a novel method for agent-based social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks.
+Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people.
+Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks.
+We then use these results to propose a collection of guidelines concerning the design of a efficient human computation system.
 \end{abstract}
@@
 
-In order to validate the algorithm as a social problem solving technique, we have modelled the collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through it and tested it over a set of {\em Sudoku} instances.
+In order to validate the algorithm as a social problem solving technique as well as establishing a comparison between agent-based simulations and tests with human subjects, we have modelled the collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through our method and tested it over a set of {\em Sudoku} instances.
 
@@
 As a result, each agent visualizes some neighbours before or after others.
-Secondly, we translated the above mathematical model into an message-selecting metric in which the solution selected by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.
+Secondly, we translated the above mathematical model into a message-selecting metric in which the solution selected by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.
 
@@
 
-In our modelling, we associate each agent with a numerical parameter determining the probability of this agent to guess when incapable of applying a typical {\em Sudoku} solving strategy.
+In our modelling, we associate each agent with a numerical parameter determining the probability this agent has to guess when incapable of applying a typical {\em Sudoku} solving strategy.
 
@@
 Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}.
-Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob}).
+This was our hypothesis, and our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob}).
 The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
@@
 Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours.
-Another chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly.
+Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly.
+Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks are able to respond positively to the employment of evaluation functions.
 
-As can be seen in Figures ~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy.
+As can be seen in Figure ~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}.
 In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution.
@@
 Even so, that behaviour was observed in human networks.
-\cite{farenzena:collabem} has suggested that human beings behave like that because in the real world the environment continuously selects against ineffective solutions, since a bad choice in solving a real world problem might cause and agent to cease communication.
+Farenzena~\cite{farenzena:collabem} has suggested that human beings behave like that because in the real world the environment continuously selects against ineffective solutions, since a bad choice in solving a real world problem might cause and agent to cease communication.
 Since neither the original experiments nor our simulation included such a mechanism, the advantages of that process have not been observed, but they might already be good enough that it may not justify the effort for the agents to evaluate the solutions.
@@
 We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes.
-With these results in mind, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.
+Thus, having in mind the fact that the strategies employed by human subjects are often not the most efficient, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.
 

### 2013-01-17 Article.tex
arrumei umas coisas

@@
 This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks.
-We present a novel method for agent-based social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks.
+We present a novel method for artificial social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks.
 Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people.
@@
 
-We have developed and detailed a novel method for agent-based social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
+We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
 It was used it to built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
@@
 We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
-We conceived a novel method for agent-based social problem solving which draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.
+We conceived a novel method for artificial social problem solving which draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.
 
-\section{A Novel Method for Agent-based Social Problem Solving}
+\section{A Novel Method for Artificial Social Problem Solving}
 
@@
 One example is the conformist behaviour studied in~\cite{cefferson:conformists} and~\cite{farenzena:collabem}.
-The proper study of these aspects demands a novel method for agent-based collaborative problem solving.
+The proper study of these aspects demands a novel method for artificial collaborative problem solving.
 
@@
 
-In order to validate the algorithm as a social problem solving technique as well as establishing a comparison between agent-based simulations and tests with human subjects, we have modelled the collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through our method and tested it over a set of {\em Sudoku} instances.
+In order to validate the algorithm as a social problem-solving technique, we have modelled the real-world collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through our method and tested it over a set of {\em Sudoku} instances, having in mind that the emergence of similar results as those observed by~\cite{farenzena:collabem} in their tests with {\em Sudoku} and {\em SAT} solving would validate our model as a good candidate for the design of social problem-solving simulations.
 
@@
 \begin{figure}
-\includegraphics[scale=0.50]{progression}
+\includegraphics[scale=0.47]{progression}
 \caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
@@
 We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments.
-To do this, we proposed a novel method for agent-based social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}.
+To do this, we proposed a novel method for artificial social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}.
 We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems.

### 2013-01-17 Article.tex
Adicionei referências, mudei pro estilo da ijcai e mais umas coisas

@@
-%\documentclass{article}
-%\usepackage{ijcai13}
+\documentclass{article}
+\usepackage{ijcai13}
+\usepackage{times}
+\usepackage{latexsym}
+
+%\documentclass[letterpaper]{article}
+%\usepackage{aaai}
 %\usepackage{times}
-%\usepackage{latexsym}
-
-\documentclass[letterpaper]{article}
-\usepackage{aaai}
-\usepackage{times}
-\usepackage{helvet}
-\usepackage{courier}
+%\usepackage{helvet}
+%\usepackage{courier}
 \usepackage{algorithm2e}
-\frenchspacing
+%\frenchspacing
 
@@
 Recently, however, there has been an increasing interest in the study of human beings as problem-solving agents.
-Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems.
+Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems as well as on the dynamics of working groups~\cite{woolley:evidencecollective}.
 However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed behaviour.
@@
 The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems.
-The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal.
+The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal ~\cite{nowak:evolutioncooperation}.
 
@@
 
-The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question.
+The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question.
 There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:
@@
 After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.
-
-\section{System Overview}
-
-We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments.
-We conceived a novel method for artificial social problem solving which draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.
 
@@
 
+\subsection{Network Topology}
+
+We modelled our agent networks through the network topologies employed by~\cite{farenzena:collabem} in their tests with human social networks.
+The topologies used were the {\em fully connected} topology, the {\em scale free} topology~\cite{barabasi:linked}, the {\em ring-2} topology and the {\em ring-3} topology~\cite{newman:newtorks}.
+
 \section{Results and Analysis}
@@
 \begin{figure}
-\includegraphics[scale=0.47]{progression}
+\includegraphics[scale=0.45]{progression}
 \caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
@@
 
-\section{Conclusions}
+\section{Conclusions and Further Work}
 
@@
 We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes.
-Thus, having in mind the fact that the strategies employed by human subjects are often not the most efficient, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.
+With these results in mind, we conjectured that some proprieties of the graphic interface (as ordering the neighbours' solutions by the value of a evaluation function) could guide human subjects into the right direction, improving the performance of the social network.
+The validation of this hypothesis has been set as our future path and is currently being pursued.
 

### 2013-01-20 Article.tex
Dei uns retoques e incrementei a análise dos gráficos

@@
 
-The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems.
+The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of collective problem-solving abilities to solve classical computer problems.
 The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal ~\cite{nowak:evolutioncooperation}.
@@
 The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question.
-There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:
-
-\begin{itemize}
-	\item Humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one.
-On the other hand,~\cite{mason:collablearnet} suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that wasn't provided.
-	\item There is a higher probability of individuals copying peers' solutions when those are shared by several neighbours.
-That behaviour is referred to by the authors as \emph{conformism}.
-A similar behaviour was observed by~\cite{mason:collablearnet}, even though the experiments used a different problem.
-\end{itemize}
+In that study a specific pattern of behaviour was observed which suggests that humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one.
+That behaviour is referred to as an evidence of conformism by the human subjects.
+On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that fact wasn't provided.
+That might mean that multiple factors might influence the behaviour of human agents.
+We analyse possible reasons for that in the \emph{Results} section.
 
@@
 We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
-It was used it to built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
+It was used to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
 For simplicity, we limited our experiments to the {\em Sudoku} problem.
@@
 For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of copying the most complete solutions.
-In order to analyse and compare this two behaviours, he have modelled each one of them as a message-selecting metric for the {\em Social Stage}.
+In order to analyse and compare these two behaviours, he have modelled each one of them as a message-selecting metric for the {\em Social Stage}.
 
@@
 
+\subsection{A Novel Method For Simulating Human Problem-Solving Networks}
+
 \subsection{Copying and Guessing are Beneficial to the Algorithm's Performance}
 
-Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}.
-This was our hypothesis, and our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob}).
-The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
-We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells.
+The authors of~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}.
+Basing ourselves in that statement, we adopted the hypothesis that a higher copy rate would improve performance of the network.
+On the other hand, regarding the process of guessing we took the opposite standing, that it would decrease performance.
+We based that hypothesis on the notion that, when an agent makes a guess, it has a high chance of filling a cell with the wrong value.
+Once that happens, that grid will assuredly be unable to lead to the right solution until the agent copies a grid without errors from one of its neighbours.
+Therefore, we hypothesised that if an agent can't make a logical move using its level of \emph{Sudoku}-solving skills, it's better for it to wait for its more capable neighbours to improve the solution and copy from them, instead of risking making and incorrect move.
+
+Regarding our first hypothesis, our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the network's performance.
+To our surprise, however, they also indicate that guessing shows no signs of being detrimental to the process.
+On the contrary, in several cases it actually contributes to advancing the solution.
+The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
+We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, not knowing the {\em Sudoku} solving rules needed to mark its cells.
 These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions.
+
+The results also differ depending on the copying strategy employed in the \emph{social stage}.
+It can be observed that the copy rate has more influence over how fast the correct solution spreads through the network if the agents are evaluating their neighbour's solutions.
+The graph in Figure~\ref{fig:copy_guess_free_most} shows that as copying increases, the number of rounds necessary for all agents to have the correct solution decreases sharply until it stabilizes in a roughly optimal level.
+Meanwhile, the benefits of guessing are much less pronounced.
+On the other hand, when the agents don't evaluate the neighbours' solutions, as can be seen in Figure~\ref{fig:copy_guess_free_prob}, their contributions don't differ as much.
+Those results confirm that the worth of copying increases when the proposed solutions are evaluated.
+
 Also, as shown in Figure~\ref{fig:copy_guess_free_prob_num_solution_reached}, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.
@@
 \includegraphics[scale=0.60]{copy_guess_free_most}
-\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric)
+\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric).
+The vertical axis represents the number of iterations needed for all the agents to find the correct solution.
 }
@@
 
-As can be seen in Figure ~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}.
+As can be seen in Figure~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed brings significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}.
 In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution.
-That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.
+That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them instead of copying an arbitrary one.
 
 The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy, and both underperformed in comparison to evaluating the solutions according to number of filled cells.
-This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of problem-solving.
+This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of social problem-solving.
 
-Even so, that behaviour was observed in human networks.
-Farenzena~\cite{farenzena:collabem} has suggested that human beings behave like that because in the real world the environment continuously selects against ineffective solutions, since a bad choice in solving a real world problem might cause and agent to cease communication.
-Since neither the original experiments nor our simulation included such a mechanism, the advantages of that process have not been observed, but they might already be good enough that it may not justify the effort for the agents to evaluate the solutions.
+Even so, that behaviour has been observed in human networks.
+In~\cite{farenzena:collabem} the authors suggest that it is justified in the real world because "in a non-virtual environment, the feedback of the environment can cause an agent to stop communicating, e.g.
+in the case of injury or death", so there would be no need for an agent to evaluate solutions because the environment is already selecting against ineffective ones.
+Since neither the original experiments nor our simulation included such a mechanism of natural selection, the advantages of that process have not been observed, but they might already be good enough that it would be unnecessary for the agents to have to spend effort evaluating the solutions.
 
@@
 One possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead using a pre-specified or random order.
-However, that might introduce a (BLANK) in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques.
+However, that might introduce an overhead in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques.
 To avoid that, perhaps simply displaying the evaluation of each solution might be enough to encourage that behaviour.

### 2013-01-21 Article.tex
Arrumei detalhes que não estavam atualizados e complementei algumas sessões

@@
 
-\cite{mason:collablearnet} also provided important insights to human cooperation.
-However, since our basis is the work of~\cite{farenzena:collabem} we will use the former's results only as secondary support.
-
 \section{Contribution}
@@
 We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
-It was used to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
-For simplicity, we limited our experiments to the {\em Sudoku} problem.
-Our goal is verifying whether the strategies employed by humans are competitive with other heuristics.
-After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.
+It was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
+We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while still remaining NP-complete and equivalent to SAT.
+Through that process, we compared the behaviour observed in humans with other strategies and reached the conclusion that it is detrimental to the problem-solving process.
+We verify that even an inaccurate metric of evaluation surpasses choosing an arbitrary neighbour to copy.
+In addition, we analyse the impact that copying and guessing have on the solving of the problem.
+After obtaining those results, we are able to propose a set of guidelines for the design of social problem-solving systems that might address those issues and improve the performance of human computing.
 
@@
 Additionally, our algorithm is composed of two stages, namely the {\em Social Stage} and the {\em Cognitive Stage}.
-
-\begin{itemize}
-\item
-Social Stage: In the {\em Social Stage}, messages are passed from agent to agent through the network connections.
-Agents are thus presented with a multiplicity of messages.
-There is a particular probability associated with the behaviour of agents choosing to copy one of these solutions in contrast to keeping their current solutions.
-We call this probability the {\em Copy Rate}.
-When an agent chooses to copy, he or she is then supposed to select for copying only one of his or her received messages.
-This is done by the means of a particular message-selecting metric.
-
-\item
-Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by the means of a heuristic or an exact method.
-\end{itemize}
 
@@
  }
- \caption{No name yet}
+ \caption{Algorithm for the proposed model, encompassing the social and cognitive stages}
 \end{algorithm}
+
+\begin{itemize}
+\item
+Social Stage: In the {\em Social Stage}, messages are passed from agent to agent through the network connections.
+Agents are thus presented with a multiplicity of messages.
+There is a particular probability associated with the behaviour of agents choosing to copy one of these solutions in contrast to keeping their current solutions.
+We call this probability the {\em Copy Rate}.
+When an agent chooses to copy, he or she is then supposed to select for copying only one of his or her received messages.
+This is done by the means of a particular message-selecting metric.
+
+\item
+Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by the means of a heuristic or an exact method.
+\end{itemize}
 
@@
 The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings.
-For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of copying the most complete solutions.
-In order to analyse and compare these two behaviours, he have modelled each one of them as a message-selecting metric for the {\em Social Stage}.
+For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of evaluating the available solutions and choosing the best according to some criterion.
+We have modelled three message-selecting strategies to employ in the \emph{Social Stage}, where the first attempts to evaluate the solutions and choose the best one, the second mimics the human behaviour of selecting the first solutions with greater probability and the third simply picks a neighbour at random to copy.
 
@@
 In the specific case of {\em Sudoku} solving, this metric selects the most filled {\em Sudoku} partial solution.
-Put in other words, it selects the {\em Sudoku} partial solution with the lesser number of blank cells.
+Put in other words, it selects the {\em Sudoku} partial solution with the least number of blank cells.
 
@@
 
+\subsubsection{{\em Pick Random} metric}
+
+This metric selects an arbitrary solution giving equal probability to each neighbour.
+
 \subsection{Cognitive Stage}
@@
 {\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature.
-Davis ~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples.
+Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles.
+Davis~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples.
 These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle.
@@
 We detail below the 'two out of three' rule.
-For details on the other $4$ rules, see ~\cite{davis:mathsudoku}.
+For details on the other $4$ rules, see~\cite{davis:mathsudoku}.
 
@@
 
-\subsection{Conformist Behaviour}
-
-We introduce in our modelling the {\em conformist} behaviour proposed by~\cite{cefferson:conformists} and further studied by~\cite{farenzena:collabem}, which states that agents are likely to copy a particular solution when surrounded by neighbours that share this solution.
-
-Our approach was to establish a {\em treshold} determining a minimum necessary quantity $N$ of neighbours sharing a particular solution.
-In our modelling, all agents with $N$ or more neighbours having a solution $s$ in common are programmed to copy solution $s$ from them.
-
 \subsection{Guessing and Backtracking}
@@
 On the other hand, the space complexity of these algorithms is a barrier to most human solvers, who need to write down tons of observations in order to employ a backtracking strategy.
-With this in mind, we propose in our modelling two different kinds of backtracking, intended to be more similar to the way human beings employ error correction in {\em Sudoku} solving in a collaborative environment such as the one analysed in~\cite{farenzena:collabem}.
-
-\begin{itemize}
-
-\item
-Local Backtracking: When faced with one or more conflicts in its own solution, an agent simply erases the conflicting cells.
-\item
-Social Backtracking: When faced with one or more conflicts in its own solution, an agent copies a solution from one of its neighbours.
+With this in mind, we propose in our modelling a different kind of backtracking, intended to be more similar to the way human beings employ error correction in {\em Sudoku} solving in a collaborative environment such as the one analysed in~\cite{farenzena:collabem}, which we refer to as \emph{social backtracking}.
+In it, when faced with one or more conflicts in its own solution, an agent copies a solution from one of its neighbours.
 In our modelling, this is done by raising the copy rate of this particular agent to $1$.
-
-\end{itemize}
 
@@
 \subsection{A Novel Method For Simulating Human Problem-Solving Networks}
+
+We have proposed a model based on social psychology to simulate human behaviour in a problem-solving social network.
+Through it, we can simulate previous experiments performed on humans by modelling the observed behaviour as the cognitive and social stages.
+That will allow us to examine the consequences of that behaviour without having to enlist human subjects, which is usually expensive and time-consuming~\cite{?}.
+Moreover this model can be used as a guide of what to look for in the data collected by the experiments, in which the strategies employed by the subjects to solve the problem individually are mapped into the cognitive stage and the metric employed to pick a neighbour to copy, into the social stage.
+
+We have applied the model into one such human computing experiment and reached particular conclusions about the methods employed by humans on it.
+Since the same behaviour was observed for different problems, we can expect these results to be generalized to a certain class of problems and systems with specific characteristics.
+We provide further analysis and details below.
 
@@
 The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
-We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, not knowing the {\em Sudoku} solving rules needed to mark its cells.
-These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions.
+We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the problem, not knowing the {\em Sudoku} solving rules needed to mark its cells.
+These agents have no hope solving the problem individually without some guessing mechanism, and the high {\em copy rates} allow them to correct wrong guesses through copying better agents' solutions.
 
@@
 Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly.
-Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks are able to respond positively to the employment of evaluation functions.
+Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks respond positively to the employment of evaluation functions.
 
@@
 Although we have used the number of filled cells as a metric, that is not guaranteed to accurately measure which solution is best, since individuals might fill in cells with the wrong value.
-That hypothesis is supported by the experiments of~\cite{mason:collablearnet}, which used optimization of multidimensional functions as the problem being solved.
+That hypothesis is supported by the experiments of~\cite{mason:collablearnet}, which used optimization of a bidimensional function as the problem being solved.
 This problem has a straightforward and accurate method of determining the fitness of a solution, which is simply the value of the given function for the proposed coordinates.
@@
 
+Our experiments, however, have shown that although completeness is not necessarily an accurate measurement of quality, it was good enough to lead the network to the right solution.
+Not only that, it consistently performed better than the other strategies, even with high guess rates.
+That means that the incorrect guesses were successfully filtered out, allowing the correct solutions to prevail.
+Those results might extend to other constraint satisfaction problems that don't have an accurate method of evaluation.
+Therefore, it is not necessary for the problem addressed to have an exact metric to compare different possible solutions.
+An imperfect metric is good enough to be employed in a problem-solving social network.
+
+Also,~\cite{mason:collablearnet} differed in that each player had exactly three neighbours.
+That fact allowed the players to see all of their neighbours at the same time in the interface, and limit their attention to less data.~\cite{farenzena:collabem} suggests that future experiments might prefer to limit their topology to smaller degrees, seeing as subjects tend to not look beyond their first few neighbours.
+It is possible for the large number of neighbours to have discouraged an in-depth evaluation of the solutions by the players.
+
 \subsection{Small Changes on the Interface Might Improve the Performance of Human Beings in Human Computation Environments}
 
-Knowing that, systems that take advantage of human computation might take advantage of the computer aspect of human computation to encourage selection of better-evaluated solutions.
-One possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead using a pre-specified or random order.
-However, that might introduce an overhead in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques.
-To avoid that, perhaps simply displaying the evaluation of each solution might be enough to encourage that behaviour.
+Considering the previous results, systems of human computation might take advantage of the interface to encourage selection of better-evaluated solutions.
+One possibility is to display the evaluation of each solution to encourage players to copy the ones with better score.
+However, the SAT experiments from~\cite{farenzena:collabem} actually assigned a score to each solution displayed to the users, who nevertheless chose according to position rather than evaluation.
+Another possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead of using a pre-specified or random order.
+
+The limitation on the network's degree suggested by~\cite{farenzena:collabem} and employed by~\cite{mason:collablearnet} is also promising, and displays evidence of success.
+Fewer connections allows for all neighbours to be displayed in the interface at once, without necessity of effort by the user by clicking buttons or scrolling.
+Moreover, humans might feel more encouraged to evaluate their neighbours if the number of possible solutions is limited.
 
@@
 We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes.
-With these results in mind, we conjectured that some proprieties of the graphic interface (as ordering the neighbours' solutions by the value of a evaluation function) could guide human subjects into the right direction, improving the performance of the social network.
+With these results in mind, we conjectured that some properties of the graphic interface (as ordering the neighbours' solutions by the value of a evaluation function) could guide human subjects into the right direction, improving the performance of the social network.
 The validation of this hypothesis has been set as our future path and is currently being pursued.

### 2013-01-23 Article.tex
Dei um jeito nas referências e retirei a imagem do sudoku do artigo
Incluí os novos gráficos das Gaussianas e falei sobre eles nos resultados

@@
 The need for trial-and-error in {\em Sudoku} puzzles is not a falsifiable conclusion, but a mathematical fact~\cite{davis:mathsudoku}.
-Some puzzles are only solvable by the means of a backtracking procedure (see Figure~\ref{fig:trial_and_error_sudoku}).
-
-\begin{figure}
-\includegraphics[scale=0.30]{trial_and_error_sudoku}
-\caption{A {\em Sudoku} puzzle solvable only by trial-and-error}
-\label{fig:trial_and_error_sudoku}
-\end{figure}
+Some puzzles are only solvable by the means of a backtracking procedure.
 
@@
 
+\begin{figure}
+\includegraphics[scale=0.60]{copy_guess_free_most}
+\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric).
+The vertical axis represents the number of iterations needed for all the agents to find the correct solution.
+}
+\label{fig:copy_guess_free_most}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.60]{copy_guess_free_prob}
+\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick among first' selection metric)
+}
+\label{fig:copy_guess_free_prob}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.60]{copy_guess_free_prob_num_solution_reached}
+\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick among first' selection metric)
+}
+\label{fig:copy_guess_free_prob_num_solution_reached}
+\end{figure}
+
 \subsection{Copying and Guessing are Beneficial to the Algorithm's Performance}
@@
 \begin{figure}
-\includegraphics[scale=0.60]{copy_guess_free_most}
-\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric).
-The vertical axis represents the number of iterations needed for all the agents to find the correct solution.
-}
-\label{fig:copy_guess_free_most}
+\includegraphics[scale=1]{ijcai_sudoku/ring}
+\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
+\label{fig:ring_gauss}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.60]{copy_guess_free_prob}
-\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick among first' selection metric)
-}
-\label{fig:copy_guess_free_prob}
+\includegraphics[scale=1]{ijcai_sudoku/sf}
+\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
+\label{fig:sf_gauss}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.60]{copy_guess_free_prob_num_solution_reached}
-\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick among first' selection metric)
-}
-\label{fig:copy_guess_free_prob_num_solution_reached}
+\includegraphics[scale=1]{ijcai_sudoku/geral}
+\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
+\label{fig:global_gauss}
 \end{figure}
 
-\subsection{Evaluating the Neighbours' Solutions is Beneficial to the Algorithm's Performance}
+\subsection{Evaluating Neighbours' Solutions is Advantageous even with an Inexact Metric}
 
@@
 
-As can be seen in Figure~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed brings significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}.
+%%As can be seen in Figure~\ref{fig:progression}, 
+Our experiments have shown that evaluating the proposed solutions indeed brings significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}.
 In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution.
@@
 
-The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy, and both underperformed in comparison to evaluating the solutions according to number of filled cells.
+The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy.
+That is to be expected because the position of each neighbour is already randomized, so there is virtually no difference between picking one of the first neighbours to copy and a random one among all.
+Seeing as the same conclusions apply to both the human and random strategies, we omit further analysis of the latter for simplicity.
+Both underperformed in comparison to evaluating the solutions according to number of filled cells.
 This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of social problem-solving.
 
-Even so, that behaviour has been observed in human networks.
-In~\cite{farenzena:collabem} the authors suggest that it is justified in the real world because "in a non-virtual environment, the feedback of the environment can cause an agent to stop communicating, e.g.
-in the case of injury or death", so there would be no need for an agent to evaluate solutions because the environment is already selecting against ineffective ones.
+We have observed in our experiments that the progress of the solution, represented by the number of agents that solve the problem in a given iteration, follows a normal distribution.
+During the first few iterations no agents have found the solution.
+Then, in a moment that varies according to the particular instance of the problem, the first few agents solve the problem.
+From that point onwards the solution starts spreading through the network.
+As more agents obtain the complete solution, more likely it becomes that further agents will copy that solution from their neighbours, according to the conformist behaviour observed in~\cite{farenzena:collabem}.
+That leads the number of agents to obtain the solution to progressively increase in the following iterations, until it reaches a point where the few remaining agents take longer to obtain the solution due to factors such as being less capable solvers or being in unfavourable positions in the topology.
+
+We have run experiments in the four different topologies enumerated above, for 7 different problem instances, and obtained similar results in each.
+The progression of the solution for the \emph{Most Filled} and \emph{First Positions} strategies can be described as normal distributions of different mean and variance.
+In the context of the experiments, the mean indicates how soon the correct solution was found, and the variance how long it took to spread through the network.
+The exact values for those parameters vary widely according to factors such as topology and problem instance, but they follow a particular pattern.
+For all cases, the strategy that evaluated solutions had lower mean, indicating the solution was found sooner, and lower variance, meaning it spread faster.
+We have chosen the scale-free and 3-ring topologies as representative examples, and plotted the average of the results for a same instance of the problem for each in Figures~\ref{fig:sf_gauss} and~\ref{fig:ring_gauss}, respectively.
+In each can be seen the percentage of agents that find the correct solution in each iteration for the two strategies, with normal curves plotted over the values, evidencing the described behaviour.
+It's noticeable that the results fluctuate more for the second strategy, which is explained by its practically random method of choosing solutions to copy.
+
+In Figure~\ref{fig:global_gauss} the average for all experiments can be seen, encompassing every topology and instance.
+In this graph, the presence of the normal behaviour in the distribution is less clear, due to it combining several different instances and topologies.
+Nevertheless, its effects can still be seen.
+The \emph{Most Filled} strategy displays different residual peaks from particular instances, while the line for the \emph{First Positions} strategy starts flattening with the accumulation of several distributions from the individual experiments.
+Most importantly, the general result of a sooner finding and faster spreading of the correct solution for the first strategy endures, showing its consistency over different scenarios.
+
+Still, even though choosing a solution based on position instead of content is provably inefficient, that behaviour has been observed in human networks.
+In~\cite{farenzena:collabem} the authors suggest that it is justified in the real world because ``in a non-virtual environment, the feedback of the environment can cause an agent to stop communicating, e.g.
+in the case of injury or death'', so there would be no need for an agent to evaluate solutions because the environment is already selecting against ineffective ones.
 Since neither the original experiments nor our simulation included such a mechanism of natural selection, the advantages of that process have not been observed, but they might already be good enough that it would be unnecessary for the agents to have to spend effort evaluating the solutions.
@@
 Moreover, humans might feel more encouraged to evaluate their neighbours if the number of possible solutions is limited.
-
-\begin{figure}
-\includegraphics[scale=0.45]{progression}
-\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
-}
-\label{fig:progression}
-\end{figure}
+%
+%\begin{figure}
+%\includegraphics[scale=0.45]{progression}
+%\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
+%}
+%\label{fig:progression}
+%\end{figure}
 

### 2013-01-24 Article.tex
Incluí as modificações que o Lamb e o Diego sugeriram
Alguns comentários eu deixei como... comentários. Pra depois a gente
passar pelo texto e ver como arrumar.

@@
 \begin{abstract}
-Social collaboration has been shown to facilitate problem-solving activity in a diverse set of environments.
-Nevertheless, if not well designed, a social human computation system may achieve results as poor as those of a single human subject performing a task.
+Social collaboration has been shown to facilitate problem-solving activity in diverse sets of environments.
+Nevertheless, if not well designed, social and human computation systems may achieve results as poor as those of a single human subject performing a task.
 This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks.
 We present a novel method for artificial social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks.
-Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people.
+Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy or mimic is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people.
 Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks.
@@
 
-For years multi-agent systems have been used to research cooperation as a tool for problem-solving.
+For years multi-agent systems have been used to research cooperation as a tool for problem-solving. %cite Malone
 Recently, however, there has been an increasing interest in the study of human beings as problem-solving agents.
 Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems as well as on the dynamics of working groups~\cite{woolley:evidencecollective}.
-However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed behaviour.
-In this paper, we use a multi-agent based simulation to complement the study of human computation, as a way of explaining the strategies used by humans and understanding their consequences in a cooperative environment.
-The control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the ones displayed by humans.
+However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed collective, human behaviour.
+In this paper, we use a multi-agent based simulation to complement %change?
+the study of human computation, as a way of explaining the strategies used by humans when solving problems and understanding their consequences in a cooperative environment.
+The degree of control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the actions and behaviours displayed by human agents.
 
 Human beings are known to be able to easily perform tasks which are still generally difficult for computers, such as natural language processing and image recognition.
-However, it would be useful to be able to apply human social computation to more straightforward computer problems with precise definitions and algorithms, but which are still computationally intensive.
-The different sets of abilities between computers and humans suggest that the latter might provide a new approach to those problems that might be more effective than current techniques employed by computers.
+%--
+However, it would be useful to apply human social computation to more straightforward computer problems with precise definitions and algorithms, but which are still computationally intensive.
+%--
+The different abilities of computers and humans suggest that the latter might provide a new approach to problems that might be more effective than current techniques employed by computers.
 That notion has been successfully applied, for example, in one of the most significant problems in the field of bioinformatics: protein structure prediction (PSP).
 A software that presents the problem to humans as an online computer game, called \emph{Foldit}~\cite{cooper:foldit}, has produced significant results in the research of PSP, which is usually approached as an optimization problem requiring extensive computational power.
-Those results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration~\cite{cooper:foldit}.
-However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional techniques.
-To take full advantage of human problem-solving strategies, we must learn their limitations.
-In order to obtain that knowledge, our system simulates human behaviour according to findings of social computation experiments.
+Such results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration~\cite{cooper:foldit}.
+However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional computational techniques.
+%--Exploit this point
+In order to take full advantage of human problem-solving strategies, we must learn their limitations.
+Humans tend to be less efficient than computers in mathematical computations, are subject to a series of physical and psychological conditions that might affect their performance, and do not always act rationally.
+We propose a model for simulating a problem-solving network of human agents.
+By applying in this model findings of experiments performed in humans, we can obtain knowledge about how human patterns of behaviour influence the problem-solving process.
+Through this system, it becomes possible to draw new conclusions from past observations of human behaviour.
+The model can be used, for example, to preview the results that changes in the infrastructure of a social computation system will have on its performance before actually performing the experiments with humans.
+Another possibility is to use the results obtained by the simulation of past experiments to plan the best configuration for a new system of social computing.
+%--Move to Contribution?
 
@@
 
-Social computation is a relatively new area of research with a diversified, interdisciplinary root that mixes social sciences, artificial intelligence, game theory and network science, among others.
-Only recently studies on the potential of human social networks for solving problems are gaining some popularity.
+Human and social computing are relatively new areas of research with a diversified, interdisciplinary root that mixes social sciences, artificial intelligence, game theory and network science, among others.
+%cite ?, Kleinberg
+Only recently studies on the potential of human social networks for solving problems are gaining some popularity. %cite Malone, Kearns
 Those have provided insights into, among other things, the impact of network structure in the collaboration process and the factors that lead neighbours' proposed solutions to be copied by individuals.
@@
 That is an idea that also appears in the Foldit game.
+%cite
 
@@
 Other initiatives have appeared, such as the ones by~\cite{farenzena:collabem} and~\cite{mason:collablearnet}, which take a different approach by having subjects trying to solve the collective problem individually, with the possibility of exchanging solutions between neighbours.
-Those have resulted in interesting conclusions on human behaviour when the possibility of copying peers makes itself present.
-It's in those models of experiments that we will focus in this work.
+Those have resulted in interesting conclusions on human behaviour when the possibility of copying peers is available.
+Our experiments follow this line of research.
 
 The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question.
+%--Make more specific
 In that study a specific pattern of behaviour was observed which suggests that humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one.
-That behaviour is referred to as an evidence of conformism by the human subjects.
-On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that fact wasn't provided.
+%--
+That behaviour is referred to as an evidence of conformism in human subjects.
+On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although %Unfortunately?
+an in-depth analysis of that fact was not reported.
 That might mean that multiple factors might influence the behaviour of human agents.
 We analyse possible reasons for that in the \emph{Results} section.
+%We also analyse possible reasons for that behaviour in the \emph{Results} section.
 
@@
 
+%--Keep?
 We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
+%--
 It was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
-We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while still remaining NP-complete and equivalent to SAT.
-Through that process, we compared the behaviour observed in humans with other strategies and reached the conclusion that it is detrimental to the problem-solving process.
+We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while being NP-complete and equivalent to SAT.
+Through that process, we compared the problem-solving strategy %strategy?
+typically used by humans with alternative, artificial strategies and reached the conclusion that it is detrimental to the problem-solving process.
+%--Explain better
 We verify that even an inaccurate metric of evaluation surpasses choosing an arbitrary neighbour to copy.
-In addition, we analyse the impact that copying and guessing have on the solving of the problem.
+%--
+In addition, we analyse the impact that copying and guessing have on the process of solving the problem.
 After obtaining those results, we are able to propose a set of guidelines for the design of social problem-solving systems that might address those issues and improve the performance of human computing.
 
-\section{A Novel Method for Artificial Social Problem Solving}
+\section{A Novel Method for %Artificial?
+Social Problem Solving}
+%P.S. method has two phases: communication and reasoning
 
@@
 
-We propose a method for solving computational problems by the means of a network of agents with social behaviour.
+We propose a method for solving computational problems by means of a network of agents endowed with social behaviour.
 Our algorithm is composed of an ordered set of $N$ agents, each encoding a partial solution to the problem, and a binary $N \times N$ matrix representing possible connections between agents.
 Additionally, our algorithm is composed of two stages, namely the {\em Social Stage} and the {\em Cognitive Stage}.
+%cite social psych
 
@@
  				$A_{j}$ = $j_{th}$ agent\;
- 				Add $A_{j}$'s solution to the collection of messages of $A_{i}$\; %A.messages.add(j.solution)\;
+ 				Add $A_{j}$'s solution to the collection of messages received by $A_{i}$\; %A.messages.add(j.solution)\;
  			}
@@
 When an agent chooses to copy, he or she is then supposed to select for copying only one of his or her received messages.
-This is done by the means of a particular message-selecting metric.
+This is done by means of a particular message-selecting strategy.
 
 \item
-Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by the means of a heuristic or an exact method.
+Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by means of a heuristic or an exact method.
 \end{itemize}
 
+%--Change focus
 \section{Performance Tests}
+%--
 
@@
 
-\subsection{Social Stage}
+\subsection{Social Stage} %Generalize!
 
@@
 
-\subsubsection{{\em Pick Most Filled} metric}
+\subsubsection{{\em Pick Most Filled} strategy}
 
@@
 
-\subsubsection{{\em Pick Among First} metric}
+\subsubsection{{\em Pick Among First} strategy}
 
@@
 
-\subsubsection{{\em Pick Random} metric}
+\subsubsection{{\em Pick Random} strategy}
 
@@
 
-{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature.
+{\em Sudoku} solving techniques are abundant in literature. %{\em Sudoku} strategy literature?
 Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles.
@@
 
-We tested the above modelling using an heterogeneous, uniform agent distribution in which every agent {\em level} ($0$ to $5$) had an equal representation in the population.
+We tested the above modelling using an heterogeneous, uniform agent distribution in which every agent {\em level} ($0$ to $5$) %explain; table?
+had an equal representation in the population.
 We performed tests with varying values for the parameters of {\em copy rate}, {\em guess rate}, {\em message selecting metric} and {\em network topology}.
@@
 \includegraphics[scale=0.60]{copy_guess_free_prob}
-\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick among first' selection metric)
+\caption{Effects of copy rate and guess rate on the collective's problem solving performance (scale-free topology with 'pick among first' selection metric)
 }
@@
 On the contrary, in several cases it actually contributes to advancing the solution.
-The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem.
+The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer rounds are needed for the agents to solve the problem.
 We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the problem, not knowing the {\em Sudoku} solving rules needed to mark its cells.
@@
 
-We have observed in our experiments that the progress of the solution, represented by the number of agents that solve the problem in a given iteration, follows a normal distribution.
-During the first few iterations no agents have found the solution.
+We have observed in our experiments that the progress of the solution, represented by the number of agents that solve the problem in a given round, follows a normal distribution.
+During the first few rounds no agents have found the solution.
 Then, in a moment that varies according to the particular instance of the problem, the first few agents solve the problem.
@@
 As more agents obtain the complete solution, more likely it becomes that further agents will copy that solution from their neighbours, according to the conformist behaviour observed in~\cite{farenzena:collabem}.
-That leads the number of agents to obtain the solution to progressively increase in the following iterations, until it reaches a point where the few remaining agents take longer to obtain the solution due to factors such as being less capable solvers or being in unfavourable positions in the topology.
+That leads the number of agents to obtain the solution to progressively increase in the following rounds, until it reaches a point where the few remaining agents take longer to obtain the solution due to factors such as being less capable solvers or being in unfavourable positions in the topology.
 
@@
 We have chosen the scale-free and 3-ring topologies as representative examples, and plotted the average of the results for a same instance of the problem for each in Figures~\ref{fig:sf_gauss} and~\ref{fig:ring_gauss}, respectively.
-In each can be seen the percentage of agents that find the correct solution in each iteration for the two strategies, with normal curves plotted over the values, evidencing the described behaviour.
+In each can be seen the percentage of agents that find the correct solution in each round for the two strategies, with normal curves plotted over the values, evidencing the described behaviour.
 It's noticeable that the results fluctuate more for the second strategy, which is explained by its practically random method of choosing solutions to copy.
@@
 Not only that, it consistently performed better than the other strategies, even with high guess rates.
+%--Explain
 That means that the incorrect guesses were successfully filtered out, allowing the correct solutions to prevail.
+%--
 Those results might extend to other constraint satisfaction problems that don't have an accurate method of evaluation.
@@
 \section{Conclusions and Further Work}
+%"An interesting, unexpected result... (filtered)"
+%Swap first two sentences
 

### 2013-01-25 Article.tex
Fiz mais umas modificações sugeridas e incluí os gráficos 3d novos feitos no GNU plot

@@
 
-\title{Social Computing Article\thanks{This title is temporary}}
+\title{Leveraging Collaboration: 
+A Methodology for the Design of Social Problem-Solving Systems}
 
@@
 Social collaboration has been shown to facilitate problem-solving activity in diverse sets of environments. 
-Nevertheless, if not well designed, social and human computation systems may achieve results as poor as those of a single human subject performing a task.
-This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks.
-We present a novel method for artificial social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks.
-Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy or mimic is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people.
-Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks.
-We then use these results to propose a collection of guidelines concerning the design of a efficient human computation system.
+Nevertheless, if not well designed, social and human computation systems may achieve results 
+only similar to those of a single human subject performing a task. 
+This scenario reflects a need for better understanding of the performance 
+issues of human problem-solving social networks. 
+We carry out several experiments on artificial social problem-solving 
+supported by results of experiments carried out with human subjects, 
+in order to analyse which parameters influence the performance of collaborative problem-solving social networks. 
+We analyse the strategies humans follow when solving a problem, 
+comparing them with alternative strategies, and 
+identify the consequences of the employed strategies 
+in the collective performance of the social network.
+Our results also indicate that copying and guessing are highly beneficial to the 
+performance of the social networks. 
+We then propose mechanisms that can improve human problem-solving abilities.
+Finally, we show that our results lead to a methodology for the design  
+of efficient problem-solving systems that can be applied 
+to several kinds of collaborative social systems. 
 \end{abstract}
@@
 %--Make more specific
-In that study a specific pattern of behaviour was observed which suggests that humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one.
-%--
+In that study a specific pattern of behaviour was observed which suggests that humans didn't evaluate the solutions proposed by their neighbours, instead choosing to copy the solutions which were displayed closer in the system's interface.
+%--Done
 That behaviour is referred to as an evidence of conformism in human subjects.
@@
 That might mean that multiple factors might influence the behaviour of human agents.
-We analyse possible reasons for that in the \emph{Results} section.
+We analyse possible reasons for that in section~\ref{sec:results}.
 %We also analyse possible reasons for that behaviour in the \emph{Results} section.
@@
 
-%--Keep?
-We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
-%--
-It was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
+We have developed a novel method for artificial social problem-solving that can be used to simulate the behaviour observed in humans in collective problem-solving systems.
+This model is described on section~\ref{sec:model}.
+
+The methodology was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
+We describe how we adapted that environment and the behaviour of its subjects to our system in section~\ref{sec:apply}.
 We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while being NP-complete and equivalent to SAT.
-Through that process, we compared the problem-solving strategy %strategy?
-typically used by humans with alternative, artificial strategies and reached the conclusion that it is detrimental to the problem-solving process.
-%--Explain better
-We verify that even an inaccurate metric of evaluation surpasses choosing an arbitrary neighbour to copy.
-%--
+However, the results obtained can be generalized to different problems.
+
+In the experiments performed by~\cite{farenzena:collabem}, it was verified that the human subjects didn't evaluate their neighbours' solutions, instead choosing an arbitrary solution based on position in the interface.
+We simulated that behaviour in our agents and compared that strategy with alternative, artificial strategies, and reached the conclusion that the human strategy is detrimental to the problem-solving process.
+A network of agents that evaluated the solutions proposed to them performed consistently better, even though the evaluation function employed wasn't one that accurately represented the solution's worth.
+That way, we verify that even a naive evaluation tactic surpasses choosing an arbitrary neighbour to copy.
+A more detailed analysis is provided in section~\ref{sec:results}.
+
 In addition, we analyse the impact that copying and guessing have on the process of solving the problem.
@@
 Social Problem Solving}
+\label{sec:model}
 %P.S. method has two phases: communication and reasoning
@@
 Our algorithm is composed of an ordered set of $N$ agents, each encoding a partial solution to the problem, and a binary $N \times N$ matrix representing possible connections between agents.
-Additionally, our algorithm is composed of two stages, namely the {\em Social Stage} and the {\em Cognitive Stage}.
+Additionally, our algorithm is composed of two stages, namely the {\em communication phase} and the {\em reasoning phase}.
 %cite social psych
@@
  	{
- 		\CommentSty{ //Social Stage }\;
+ 		\CommentSty{ //Communication Phase }\;
  		$A_{i}$ = $i_{th}$ agent\;
@@
  	{
- 		\CommentSty{ //Cognitive Stage }\;
+ 		\CommentSty{ //Reasoning Phase }\;
  		$A_{i}$ = $i_{th}$ agent\;
@@
  }
- \caption{Algorithm for the proposed model, encompassing the social and cognitive stages}
+ \caption{Algorithm for the proposed model, encompassing the communication and reasoning phases}
 \end{algorithm}
@@
 \item
-Social Stage: In the {\em Social Stage}, messages are passed from agent to agent through the network connections.
+Communication phase: In the {\em communication phase}, messages are passed from agent to agent through the network connections.
 Agents are thus presented with a multiplicity of messages.
@@
 We call this probability the {\em Copy Rate}.
-When an agent chooses to copy, he or she is then supposed to select for copying only one of his or her received messages.
+When an agent chooses to copy, it is then supposed to select for copying a single one of its received messages.
 This is done by means of a particular message-selecting strategy.
@@
 \item
-Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by means of a heuristic or an exact method.
+Reasoning phase: In the {\em reasoning phase}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by means of a heuristic or an exact method.
 \end{itemize}
@@
 \section{Performance Tests}
+\label{sec:apply}
 %--
@@
 
-\subsection{Social Stage} %Generalize!
+\subsection{Communication Phase} %Generalize!
 
 The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings.
-For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of evaluating the available solutions and choosing the best according to some criterion.
-We have modelled three message-selecting strategies to employ in the \emph{Social Stage}, where the first attempts to evaluate the solutions and choose the best one, the second mimics the human behaviour of selecting the first solutions with greater probability and the third simply picks a neighbour at random to copy.
+For instance, the authors' analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of evaluating the available solutions and choosing the best according to some criterion.
+We have modelled three message-selecting strategies to employ in the \emph{communication phase}, where the first attempts to evaluate the solutions and choose the best one, the second mimics the human behaviour of selecting the first solutions with greater probability and the third simply picks a neighbour at random to copy.
 
-\subsubsection{{\em Pick Most Filled} strategy}
+\subsubsection{{\em Most Filled} strategy}
 
@@
 
-\subsubsection{{\em Pick Among First} strategy}
+%This is not an accurate measurement of fitness
+
+\subsubsection{{\em First Positions} strategy}
 
@@
 
-\subsubsection{{\em Pick Random} strategy}
+\subsubsection{{\em Random} strategy}
 
@@
 
-\subsection{Cognitive Stage}
+Although used here in the context of the \emph{Sudoku} problem, these strategies can be generalized to apply to different problems.
+It was verified in~\cite{farenzena:collabem} that the human behaviour of copying arbitrary solutions was not strictly dependent on the problem, since similar results were obtained for both SAT and \emph{Sudoku}.
+Meanwhile, the \emph{Most Filled} strategy can be adapted appropriately to the relevant problem.
+For example, in solving the SAT problem one can evaluate solutions by counting the number of clauses that evaluate to \emph{true}.
 
-{\em Sudoku} solving techniques are abundant in literature. %{\em Sudoku} strategy literature?
+\subsection{Reasoning Phase}
+
+The techniques employed by the agents to advance the solution individually should be chosen according to the problem in question.
+In the case of {\em Sudoku}, solving techniques are abundant in literature.
+%{\em Sudoku} strategy literature?
 Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles.
@@
 We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}.
-These functions can be used in the {\em Cognitive Stage} to add local changes to the {\em Sudoku} message received in the {\em Social Stage}.
+These functions can be used in the {\em reasoning phase} to add local changes to the {\em Sudoku} message received in the {\em communication phase}.
 
@@
 
+%--Keep?
 \subsection{Copying Solutions}
@@
 We incorporated this copying frequency into our modelling, recreating the scenario of the experiments conducted by~\cite{farenzena:collabem} by setting this parameter accordingly to the topologies we used.
+%--
 
@@
 \section{Results and Analysis}
+\label{sec:results}
 
@@
 We have proposed a model based on social psychology to simulate human behaviour in a problem-solving social network.
-Through it, we can simulate previous experiments performed on humans by modelling the observed behaviour as the cognitive and social stages.
+Through it, we can simulate previous experiments performed on humans by modelling the observed behaviour as the reasoning and communication phases.
 That will allow us to examine the consequences of that behaviour without having to enlist human subjects, which is usually expensive and time-consuming~\cite{?}.
-Moreover this model can be used as a guide of what to look for in the data collected by the experiments, in which the strategies employed by the subjects to solve the problem individually are mapped into the cognitive stage and the metric employed to pick a neighbour to copy, into the social stage.
+Moreover this model can be used as a guide of what to look for in the data collected by the experiments, in which the strategies employed by the subjects to solve the problem individually are mapped into the reasoning phase and the metric employed to pick a neighbour to copy, into the communication phase.
 
@@
 \begin{figure}
-\includegraphics[scale=0.60]{copy_guess_free_most}
+\includegraphics[scale=1]{ijcai_sudoku/fill_iter}
 \caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric).
@@
 \begin{figure}
-\includegraphics[scale=0.60]{copy_guess_free_prob}
+\includegraphics[scale=1]{ijcai_sudoku/fill_suc}
+\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick most filled' selection metric).
+}
+\label{fig:copy_guess_free_most}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=1]{ijcai_sudoku/first_iter}
 \caption{Effects of copy rate and guess rate on the collective's problem solving performance (scale-free topology with 'pick among first' selection metric)
@@
 \begin{figure}
-\includegraphics[scale=0.60]{copy_guess_free_prob_num_solution_reached}
+\includegraphics[scale=1]{ijcai_sudoku/first_suc}
 \caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick among first' selection metric)
@@
 
-The results also differ depending on the copying strategy employed in the \emph{social stage}.
+The results also differ depending on the copying strategy employed in the \emph{communication phase}.
 It can be observed that the copy rate has more influence over how fast the correct solution spreads through the network if the agents are evaluating their neighbour's solutions.
@@
 
-Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours.
+Of the three metrics employed by us in the \emph{communication phase}, only one had the agent evaluate the content of the solutions proposed by their neighbours.
 Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly.

### 2013-01-27 Article.tex
Reorganizei as sessões de acordo com sugestões, separei a sessão de Resultados em duas, com uma nova sessão para Discussão

@@
 issues of human problem-solving social networks. 
-We carry out several experiments on artificial social problem-solving 
+Firstly, we propose a model for simulating social problem-solving. 
+We then carry out several simulations with artificial agents  
 supported by results of experiments carried out with human subjects, 
@@
 We analyse the strategies humans follow when solving a problem, 
-comparing them with alternative strategies, and 
+comparing them with alternative ones, and 
 identify the consequences of the employed strategies 
 in the collective performance of the social network. 
-Our results also indicate that copying and guessing are highly beneficial to the 
+Our results also indicate that copying and guessing are beneficial to the 
 performance of the social networks. 
-We then propose mechanisms that can improve human problem-solving abilities.
+We then propose mechanisms that can improve 
+collaborative problem-solving.
 Finally, we show that our results lead to a methodology for the design  
@@
 to several kinds of collaborative social systems.
+
 \end{abstract}
@@
 
+%--Contextualização geral
 For years multi-agent systems have been used to research cooperation as a tool for problem-solving. %cite Malone
@@
 Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems as well as on the dynamics of working groups~\cite{woolley:evidencecollective}.
+
+%--O problema, por que ele é importante
 However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed collective, human behaviour.
-In this paper, we use a multi-agent based simulation to complement %change?
-the study of human computation, as a way of explaining the strategies used by humans when solving problems and understanding their consequences in a cooperative environment.
-The degree of control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the actions and behaviours displayed by human agents.
+In order to better employ human abilities to problem-solving, we need a method of studying that behaviour and its consequences.
 
@@
 However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional computational techniques.
-%--Exploit this point
+
 In order to take full advantage of human problem-solving strategies, we must learn their limitations.
 Humans tend to be less efficient than computers in mathematical computations, are subject to a series of physical and psychological conditions that might affect their performance, and do not always act rationally.
-We propose a model for simulating a problem-solving network of human agents.
-By applying in this model findings of experiments performed in humans, we can obtain knowledge about how human patterns of behaviour influence the problem-solving process.
+Those are all factors that might come in the way of the problem-solving process, but by understanding their consequences we can find ways to sidestep them or even use them in our favour.
+
+%--Como nós vamos resolver
+In this paper, we use a multi-agent based simulation to complement %change?
+the study of human computation, as a way of explaining the strategies used by humans when solving problems and understanding their consequences in a cooperative environment.
+The degree of control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the actions and behaviours displayed by human agents.
+
 Through this system, it becomes possible to draw new conclusions from past observations of human behaviour.
 The model can be used, for example, to preview the results that changes in the infrastructure of a social computation system will have on its performance before actually performing the experiments with humans.
-Another possibility is to use the results obtained by the simulation of past experiments to plan the best configuration for a new system of social computing.
-%--Move to Contribution?
+Another possibility is to use the results obtained by the simulation of past experiments to plan the configuration of a new system of social computing.
 
@@
 The origin of human computation as we know it today can be traced back to the work of~\cite{vonahm:gwap}, which identified the possibility of using entertainment as an incentive to participation of human subjects, applying it in games in which the participants are actually performing a computation.
-That is an idea that also appears in the Foldit game.
-%cite
+That is an idea that also appears in the Foldit game~\cite{cooper:foldit}.
 
 The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of collective problem-solving abilities to solve classical computer problems.
-The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal ~\cite{nowak:evolutioncooperation}.
+The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal~\cite{nowak:evolutioncooperation}.
 
@@
 The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question.
-%--Make more specific
 In that study a specific pattern of behaviour was observed which suggests that humans didn't evaluate the solutions proposed by their neighbours, instead choosing to copy the solutions which were displayed closer in the system's interface.
-%--Done
 That behaviour is referred to as an evidence of conformism in human subjects.
 On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although %Unfortunately?
-an in-depth analysis of that fact was not reported.
-That might mean that multiple factors might influence the behaviour of human agents.
-We analyse possible reasons for that in section~\ref{sec:results}.
-%We also analyse possible reasons for that behaviour in the \emph{Results} section.
+an in-depth analysis of that fact was not reported. That might mean that multiple factors might influence the behaviour of human agents. We analyse possible reasons in section~\ref{sec:discuss}.
 
@@
 
-We have developed a novel method for artificial social problem-solving that can be used to simulate the behaviour observed in humans in collective problem-solving systems.
+%--Principais resultados
+We developed a novel method for artificial social problem-solving that can be used to simulate the behaviour observed in humans in collective problem-solving systems.
 This model is described on section~\ref{sec:model}.
@@
 The methodology was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them.
-We describe how we adapted that environment and the behaviour of its subjects to our system in section~\ref{sec:apply}.
-We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while being NP-complete and equivalent to SAT.
+We describe how we adapted that environment and the behaviour of its subjects to our system in section~\ref{sec:setup}.
+We limited our experiments to the Sudoku problem, which is more attractive and accessible to human beings while being NP-complete and equivalent to SAT.
 However, the results obtained can be generalized to different problems.
@@
 In the experiments performed by~\cite{farenzena:collabem}, it was verified that the human subjects didn't evaluate their neighbours' solutions, instead choosing an arbitrary solution based on position in the interface.
-We simulated that behaviour in our agents and compared that strategy with alternative, artificial strategies, and reached the conclusion that the human strategy is detrimental to the problem-solving process.
+We simulated that behaviour in our agents and compared that strategy with an alternative, artificial strategy, and reached the conclusion that the human strategy is detrimental to the problem-solving process.
 A network of agents that evaluated the solutions proposed to them performed consistently better, even though the evaluation function employed wasn't one that accurately represented the solution's worth.
 That way, we verify that even a naive evaluation tactic surpasses choosing an arbitrary neighbour to copy.
-A more detailed analysis is provided in section~\ref{sec:results}.
-
-In addition, we analyse the impact that copying and guessing have on the process of solving the problem.
+A more detailed analysis is provided in sections~\ref{sec:results} and~\ref{sec:discuss}.
+In the same section, we analyse the impact that copying and guessing have on the process of solving the problem.
 After obtaining those results, we are able to propose a set of guidelines for the design of social problem-solving systems that might address those issues and improve the performance of human computing.
@@
 \label{sec:model}
-%P.S. method has two phases: communication and reasoning
 
@@
 Additionally, our algorithm is composed of two stages, namely the {\em communication phase} and the {\em reasoning phase}.
-%cite social psych
 
@@
 \item
-Communication phase: In the {\em communication phase}, messages are passed from agent to agent through the network connections.
+Communication phase: In the communication phase, messages are passed from agent to agent through the network connections.
 Agents are thus presented with a multiplicity of messages.
 There is a particular probability associated with the behaviour of agents choosing to copy one of these solutions in contrast to keeping their current solutions.
-We call this probability the {\em Copy Rate}.
+We call this probability the \emph{copy rate}.
 When an agent chooses to copy, it is then supposed to select for copying a single one of its received messages.
@@
 \item
-Reasoning phase: In the {\em reasoning phase}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by means of a heuristic or an exact method.
+Reasoning phase: In the reasoning phase, agents are supposed to add local changes to the messages copied in the previous stage. This is done by means of a heuristic or an exact method.
 \end{itemize}
 
-%--Change focus
-\section{Performance Tests}
-\label{sec:apply}
-%--
+\section{Experimental Setup}
+\label{sec:setup}
 
-In order to validate the algorithm as a social problem-solving technique, we have modelled the real-world collaborative {\em Sudoku} solving environment studied in~\cite{farenzena:collabem} through our method and tested it over a set of {\em Sudoku} instances, having in mind that the emergence of similar results as those observed by~\cite{farenzena:collabem} in their tests with {\em Sudoku} and {\em SAT} solving would validate our model as a good candidate for the design of social problem-solving simulations.
+In order to validate our method as a social problem-solving model, we have modelled the real-world collaborative Sudoku solving environment studied in~\cite{farenzena:collabem} through our method and tested it over a set of Sudoku instances.
 
-\subsection{Communication Phase} %Generalize!
+\subsection{Communication Phase}
 
@@
 For instance, the authors' analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of evaluating the available solutions and choosing the best according to some criterion.
-We have modelled three message-selecting strategies to employ in the \emph{communication phase}, where the first attempts to evaluate the solutions and choose the best one, the second mimics the human behaviour of selecting the first solutions with greater probability and the third simply picks a neighbour at random to copy.
+We have modelled two message-selecting strategies to employ in the communication phase, where one attempts to evaluate the solutions and choose the best one and the other mimics the human behaviour of selecting the first solutions with greater probability.
+
+Although employed by us in the context of the Sudoku problem, these strategies can be generalized to apply to different problems.
+It was verified in~\cite{farenzena:collabem} that the human behaviour of copying arbitrary solutions was not strictly dependent on the problem, since similar results were obtained for both SAT and Sudoku.
 
@@
 
-This metric employs the intuitive strategy of selecting the most complete message for copying.
-In the specific case of {\em Sudoku} solving, this metric selects the most filled {\em Sudoku} partial solution.
-Put in other words, it selects the {\em Sudoku} partial solution with the least number of blank cells.
-
-%This is not an accurate measurement of fitness
+This strategy employs the intuitive strategy of selecting the most complete message for copying.
+For example, in the SAT problem the most complete solution could be the one with the most clauses that evaluate to \emph{true}.
+In the specific case of Sudoku solving, this strategy selects the most filled Sudoku partial solution.
+Put in other words, it selects the Sudoku partial solution with the least number of blank cells.
+This is an attempt at a strategy that evaluates the messages that arrive to the agent and chooses the best solution.
+It is important to notice, however, that it doesn't guarantee that the chosen solution is actually better, since it might contain errors.
+In the case of Sudoku, a cell might be marked with wrong value.
 
@@
 As a result, each agent visualizes some neighbours before or after others.
-Secondly, we translated the above mathematical model into a message-selecting metric in which the solution selected by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.
-
-\subsubsection{{\em Random} strategy}
-
-This metric selects an arbitrary solution giving equal probability to each neighbour.
-
-Although used here in the context of the \emph{Sudoku} problem, these strategies can be generalized to apply to different problems.
-It was verified in~\cite{farenzena:collabem} that the human behaviour of copying arbitrary solutions was not strictly dependent on the problem, since similar results were obtained for both SAT and \emph{Sudoku}.
-Meanwhile, the \emph{Most Filled} strategy can be adapted appropriately to the relevant problem.
-For example, in solving the SAT problem one can evaluate solutions by counting the number of clauses that evaluate to \emph{true}.
+Secondly, we translated the above mathematical model into a message-selecting strategy in which the solution selected by an agent is the $k_{th}$ with probability $\langle X(k)\rangle$.
 
@@
 The techniques employed by the agents to advance the solution individually should be chosen according to the problem in question.
-In the case of {\em Sudoku}, solving techniques are abundant in literature.
-%{\em Sudoku} strategy literature?
-Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles.
+In the case of Sudoku, solving techniques are abundant in literature.
+%Sudoku strategy literature?
+These techniques are based on the reasoning usually employed by humans to solve Sudoku puzzles.
 Davis~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples.
-These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle.
-We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}.
-These functions can be used in the {\em reasoning phase} to add local changes to the {\em Sudoku} message received in the {\em communication phase}.
+These techniques intend to, given a partial Sudoku solution, generate a set of {\em movements} which can be used to mark cells of this Sudoku puzzle.
+We implemented five of these rules, modelling each one of them as a function that maps a Sudoku partial solution to a set of movements.
+These functions can be used in the reasoning phase to add local changes to the Sudoku message received in the communication phase.
 
@@
 In our modelling, each agent knows a particular quantity of rules, this quantity determining the agent's {\em level}.
-Our tests were all conducted with a heterogeneous population of agents of different {\em levels}.
+For instance, an agent of level 3 knows three out of the five rules.
+Agents of level 0 know no rules and therefore can only guess and copy.
+That way, we model a wide range of skills that might be found in human agents.
+Our tests were all conducted with a heterogeneous population of agents of different levels.
 We detail below the 'two out of three' rule.
-For details on the other $4$ rules, see~\cite{davis:mathsudoku}.
+For details on the other four rules, see~\cite{davis:mathsudoku}.
 
@@
 It aims to find a value $v$ such that $v$ is present in two of the three $3 \times 3$ blocks encompassed by the group, but missing on the third.
-It proceeds by enumerating all the candidate cells - namely the empty cells - on this block, and then, by eliminating from this set all the cells that are encompassed by the rows or columns in which $v$ is placed on the other two blocks.
+It proceeds by enumerating all the candidate cells - namely the empty cells - on this block, and then, by eliminating from this set all the cells that belong to the rows or columns in which $v$ is placed on the other two blocks.
 If the resulting set has cardinality $1$, the rule has successfully found a cell to mark.
@@
 
-In a study conducted by~\cite{farenzena:collabem}, subjects were invited to solve {\em Sudoku} puzzles and share them with other subjects with whom they were connected through a network topology.
+In the study conducted by~\cite{farenzena:collabem}, subjects were invited to solve Sudoku puzzles and share them with other subjects with whom they were connected through a network topology.
 At any time, a player could copy solutions from one of his or her neighbours.
@@
 
-We have consistent evidence that trial-and-error is a part of the {\em Sudoku} solving experience.
-The need for trial-and-error in {\em Sudoku} puzzles is not a falsifiable conclusion, but a mathematical fact~\cite{davis:mathsudoku}.
+We have consistent evidence that trial-and-error is a part of the Sudoku solving experience.
+The need for trial-and-error in Sudoku puzzles is not a falsifiable conclusion, but a mathematical fact~\cite{davis:mathsudoku}.
 Some puzzles are only solvable by the means of a backtracking procedure.
 
-In our modelling, we associate each agent with a numerical parameter determining the probability this agent has to guess when incapable of applying a typical {\em Sudoku} solving strategy.
+In our modelling, we associate each agent with a numerical parameter determining the probability this agent has to guess when incapable of applying a typical Sudoku solving strategy.
+We call this parameter the \emph{guess rate}.
 
-Automatic {\em Sudoku} solvers employing a backtracking algorithm are easily programmed and very time-efficient.
+Automatic Sudoku solvers employing a backtracking algorithm are easily programmed and very time-efficient.
 On the other hand, the space complexity of these algorithms is a barrier to most human solvers, who need to write down tons of observations in order to employ a backtracking strategy.
-With this in mind, we propose in our modelling a different kind of backtracking, intended to be more similar to the way human beings employ error correction in {\em Sudoku} solving in a collaborative environment such as the one analysed in~\cite{farenzena:collabem}, which we refer to as \emph{social backtracking}.
+With this in mind, we propose in our modelling a different kind of backtracking, intended to be more similar to the way human beings employ error correction in Sudoku solving in a collaborative environment such as the one analysed in~\cite{farenzena:collabem}, which we refer to as \emph{social backtracking}.
 In it, when faced with one or more conflicts in its own solution, an agent copies a solution from one of its neighbours.
-In our modelling, this is done by raising the copy rate of this particular agent to $1$.
+In our modelling, this is done by raising the copy rate of this particular agent to $100 \%$.
 
@@
 We modelled our agent networks through the network topologies employed by~\cite{farenzena:collabem} in their tests with human social networks.
-The topologies used were the {\em fully connected} topology, the {\em scale free} topology~\cite{barabasi:linked}, the {\em ring-2} topology and the {\em ring-3} topology~\cite{newman:newtorks}.
+The topologies used were the {\em fully connected} topology, the {\em scale-free} topology~\cite{barabasi:linked}, the {\em 2-Ring} topology and the {\em 3-Ring} topology~\cite{newman:newtorks}.
 
-\section{Results and Analysis}
+\section{Experiments and Results}
 \label{sec:results}
 
-We tested the above modelling using an heterogeneous, uniform agent distribution in which every agent {\em level} ($0$ to $5$) %explain; table?
-had an equal representation in the population.
-We performed tests with varying values for the parameters of {\em copy rate}, {\em guess rate}, {\em message selecting metric} and {\em network topology}.
+We tested the simulated Sudoku environment using an heterogeneous, uniform agent distribution in which every agent level (0 to 5) %explain; table?
+had an equal representation in the population. We performed experiments with varying message selecting strategies, network topologies and values for the parameters of copy rate and guess rate.
 
-\subsection{A Novel Method For Simulating Human Problem-Solving Networks}
+\begin{figure}
+\includegraphics[scale=1]{ijcai_sudoku/ring}
+\caption{The graph presents the average results for the 3-ring topology, showing the proportion of agents to obtain the correct solution on each round for both the \emph{Most Filled} and \emph{First Positions} strategies.
+The lines for both strategies can be fitted to normal distributions with different values for mean and variance.}
+\label{fig:ring_gauss}
+\end{figure}
 
-We have proposed a model based on social psychology to simulate human behaviour in a problem-solving social network.
-Through it, we can simulate previous experiments performed on humans by modelling the observed behaviour as the reasoning and communication phases.
-That will allow us to examine the consequences of that behaviour without having to enlist human subjects, which is usually expensive and time-consuming~\cite{?}.
-Moreover this model can be used as a guide of what to look for in the data collected by the experiments, in which the strategies employed by the subjects to solve the problem individually are mapped into the reasoning phase and the metric employed to pick a neighbour to copy, into the communication phase.
+\begin{figure}
+\includegraphics[scale=1]{ijcai_sudoku/sf}
+\caption{The graph presents the average results for the scale-free topology, showing the proportion of agents to obtain the correct solution on each round for both the \emph{Most Filled} and \emph{First Positions} strategies.
+The lines for both strategies can be fitted to normal distributions with different values for mean and variance.}
+\label{fig:sf_gauss}
+\end{figure}
 
-We have applied the model into one such human computing experiment and reached particular conclusions about the methods employed by humans on it.
-Since the same behaviour was observed for different problems, we can expect these results to be generalized to a certain class of problems and systems with specific characteristics.
-We provide further analysis and details below.
+\begin{figure}
+\includegraphics[scale=1]{ijcai_sudoku/geral}
+\caption{The graph presents the average results for all topologies and instances, showing the proportion of agents to obtain the correct solution on each round for both the \emph{Most Filled} and \emph{First Positions} strategies.
+The lines for both strategies can be fitted to normal distributions with different values for mean and variance.}
+\label{fig:global_gauss}
+\end{figure}
+
+\subsection{Comparison of Copying Strategies}
+
+%--Descrever experimentos
+We have run experiments with four different topologies, previously enumerated in section~\ref{sec:setup}, for seven different problem instances, and obtained similar results in each.
+We used fixed values of copy rate and guess rate in all runs.
+Each experiment ran for 100 rounds composed of a communication phase and a reasoning phase.
+For each combination of topology and instance we ran once using the \emph{Most Filled} strategy and again using the \emph{First Positions} strategy, with the goal of comparing their performance.
+Our hypothesis was that the \emph{Most Filled} strategy would perform better, a result which would confirm our belief that problem-solving social networks respond positively to the employment of evaluation functions.
+
+%--Descrever resultados
+We have observed in our experiments that the progress of the solution, represented by the number of agents that solve the problem in a given round, follows a normal distribution.
+During the first rounds no agents have found the solution.
+Then the first few agents solve the problem.
+The round in which that happens varies according to the particular instance of the problem.
+From that point onwards the final solution starts spreading throughout the network.
+As more agents obtain the complete solution, it becomes more likely that further agents will copy that solution from their neighbour, which complies with a conformist behaviour, as observed in~\cite{farenzena:collabem}.
+The number of agents with complete solutions increases in the following rounds, until it reaches a point where the few remaining agents take longer to obtain the solution due to factors such as being less skilled solvers or being in unfavourable positions in the topology.
+
+The solution progress for the \emph{Most Filled} and \emph{First Positions} strategies can be described as normal distributions of different mean and variance.
+In the experiments, the mean indicates how soon the correct solution was found, and the variance how long the final solution took to spread throughout the network.
+The exact values for those parameters vary according to factors such as topology and problem instance, but they follow a particular pattern: in all cases, the \emph{Most Filled} strategy has lower mean - indicating the solution is found sooner - and lower variance - meaning it spreads faster.
+We have chosen the scale-free and 3-ring topologies as representative examples, and plotted the average of the results for the same instance of the problem for each topology in Fig.~\ref{fig:ring_gauss} and~\ref{fig:sf_gauss}, respectively.
+Each graph shows the average of the percentage of agents that find the correct solution in each round for the two strategies, with normal curves plotted over the values evidencing the behaviour described above.
+One notes that the results fluctuate more for the second strategy, which is explained by its nearly random method of choosing solutions to copy.
+
+Fig.~\ref{fig:global_gauss} depicts the average for all experiments, encompassing every topology and instance.
+In this graph, the presence of the normal behaviour in the distribution is less clear, because it combines several different instances and topologies.
+Nevertheless, its effects can still be seen.
+The \emph{Most Filled} strategy displays different residual peaks from particular instances, while the line for the \emph{First Positions} strategy starts flattening with the accumulation of several distributions from the individual experiments.
+More importantly,
+Fig.~\ref{fig:global_gauss} shows that the results of Fig.~\ref{fig:ring_gauss} and~\ref{fig:sf_gauss} can be generalized: in average, for every topology and instance, the network converged to the correct solution between rounds 44 and 60 with the \emph{Most Filled} strategy, and between rounds 54 and 94 with the \emph{First Positions} strategy, showing that for the \emph{Most Filled} strategy the solution is found earlier and spreads faster.
 
@@
 \includegraphics[scale=1]{ijcai_sudoku/fill_iter}
-\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric).
-The vertical axis represents the number of iterations needed for all the agents to find the correct solution.
+\caption{The graph shows the average number of iterations needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{Most Filled} strategy.
 }
-\label{fig:copy_guess_free_most}
+\label{fig:fill_iter}
 \end{figure}
@@
 \includegraphics[scale=1]{ijcai_sudoku/fill_suc}
-\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick most filled' selection metric).
+\caption{The graph shows the number of experiments in which all agents obtained the correct solution, for a given value of copy rate and guess rate when using the \emph{Most Filled} strategy.
 }
-\label{fig:copy_guess_free_most}
+\label{fig:fill_suc}
 \end{figure}
@@
 \includegraphics[scale=1]{ijcai_sudoku/first_iter}
-\caption{Effects of copy rate and guess rate on the collective's problem solving performance (scale-free topology with 'pick among first' selection metric)
+\caption{The graph shows the average number of iterations needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{First Positions} strategy.
 }
-\label{fig:copy_guess_free_prob}
+\label{fig:first_iter}
 \end{figure}
@@
 \includegraphics[scale=1]{ijcai_sudoku/first_suc}
-\caption{Effects of copy rate and guess rate on the algorithm's convergence (scale-free topology with 'pick among first' selection metric)
+\caption{The graph shows the number of experiments in which all agents obtained the correct solution, for a given value of copy rate and guess rate when using the \emph{First Positions} strategy.
 }
-\label{fig:copy_guess_free_prob_num_solution_reached}
+\label{fig:first_suc}
 \end{figure}
 
-\subsection{Copying and Guessing are Beneficial to the Algorithm's Performance}
+\subsection{Variation in Copy Rate and Guess Rate}
 
+%--Descrever experimentos
 The authors of~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}.
@@
 Once that happens, that grid will assuredly be unable to lead to the right solution until the agent copies a grid without errors from one of its neighbours.
-Therefore, we hypothesised that if an agent can't make a logical move using its level of \emph{Sudoku}-solving skills, it's better for it to wait for its more capable neighbours to improve the solution and copy from them, instead of risking making and incorrect move.
+Therefore, we hypothesised that if an agent cannot make a logical move using its level of Sudoku-solving skills, it is better for it to wait for its neighbours to improve the solution and copy from them, instead of risking making an incorrect move.
 
-Regarding our first hypothesis, our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the network's performance.
-To our surprise, however, they also indicate that guessing shows no signs of being detrimental to the process.
-On the contrary, in several cases it actually contributes to advancing the solution.
-The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer rounds are needed for the agents to solve the problem.
-We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the problem, not knowing the {\em Sudoku} solving rules needed to mark its cells.
-These agents have no hope solving the problem individually without some guessing mechanism, and the high {\em copy rates} allow them to correct wrong guesses through copying better agents' solutions.
+In order to test our hypotheses, we repeated our experiments for the same four topologies, this time varying the copy rate and guess rate between $0\%$ and $100\%$ each.
+From our results for each topology, we plotted two surfaces for each strategy.
+The first shows the average number of iterations needed for the network to converge to the correct solution, and the second the number of experiments in which every agent obtained the correct solution in the limit of 100 rounds.
 
-The results also differ depending on the copying strategy employed in the \emph{communication phase}.
-It can be observed that the copy rate has more influence over how fast the correct solution spreads through the network if the agents are evaluating their neighbour's solutions.
-The graph in Figure~\ref{fig:copy_guess_free_most} shows that as copying increases, the number of rounds necessary for all agents to have the correct solution decreases sharply until it stabilizes in a roughly optimal level.
+%--Descrever resultados
+Fig.~\ref{fig:fill_iter} and Fig.~\ref{fig:first_iter} show the average number of rounds needed for the network to converge to the correct solution for the \emph{Most Filled} and \emph{First Positions} strategy, respectively.
+They both show a maximum in (copy rate: 0, guess rate: 0) and a minimum in (copy rate: 100, guess rate: 100), with greater copy rate and guess rate decreasing the number of rounds needed for the agents to solve the problem.
+
+The results also differ depending on the copying strategy employed in the communication phase.
+Fig.~\ref{fig:fill_iter} shows that, using the \emph{Most Filled} strategy, as copying increases the number of rounds needed for all agents to have the correct solution decreases sharply until it stabilizes in a roughly optimal level.
+Similarly, in Fig.~\ref{fig:fill_suc} the number of experiments in which every agent obtains the correct solution rises fast as copying increases.
 Meanwhile, the benefits of guessing are much less pronounced.
-On the other hand, when the agents don't evaluate the neighbours' solutions, as can be seen in Figure~\ref{fig:copy_guess_free_prob}, their contributions don't differ as much.
-Those results confirm that the worth of copying increases when the proposed solutions are evaluated.
+On the other hand, when the agents don't evaluate the neighbours' solutions, as can be seen in Fig.~\ref{fig:first_iter} and Fig.~\ref{fig:first_suc}, their contributions don't differ as much.
 
-Also, as shown in Figure~\ref{fig:copy_guess_free_prob_num_solution_reached}, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.
+\section{Discussion}
+\label{sec:discuss}
 
-\begin{figure}
-\includegraphics[scale=1]{ijcai_sudoku/ring}
-\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
-\label{fig:ring_gauss}
-\end{figure}
+\subsection{A Novel Method For Simulating Human Problem-Solving Networks}
 
-\begin{figure}
-\includegraphics[scale=1]{ijcai_sudoku/sf}
-\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
-\label{fig:sf_gauss}
-\end{figure}
+We have proposed a model to simulate human behaviour in a problem-solving social network.
+Through it, one can simulate previous experiments performed on humans by modelling the observed behaviour as the reasoning and communication phases.
+That way, one can examine the consequences of that behaviour without having to enlist human subjects, which is usually expensive and time-consuming~\cite{?}.
+Moreover this model can be used as a guide of what to look for in the data collected by the experiments, in which the strategies employed by the subjects to solve the problem individually are mapped into the reasoning phase and the strategy employed to pick a neighbour to copy, into the communication phase.
 
-\begin{figure}
-\includegraphics[scale=1]{ijcai_sudoku/geral}
-\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)}
-\label{fig:global_gauss}
-\end{figure}
+We have applied the model into one such human computing experiment and reached particular conclusions about the methods employed on it by humans.
+Since the same behaviour was observed for different problems, we can expect these results to be generalized to a certain class of problems and systems with specific characteristics.
+We provide further analysis below.
 
-\subsection{Evaluating Neighbours' Solutions is Advantageous even with an Inexact Metric}
+\subsection{Evaluating Neighbours' Solutions is Advantageous}
 
-Of the three metrics employed by us in the \emph{communication phase}, only one had the agent evaluate the content of the solutions proposed by their neighbours.
-Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly.
-Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks respond positively to the employment of evaluation functions.
-
-%%As can be seen in Figure~\ref{fig:progression}, 
-Our experiments have shown that evaluating the proposed solutions indeed brings significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}.
+Our comparison between the \emph{Most Filled} and \emph{First Positions} strategies has shown that evaluating the neighbours' proposed solutions indeed brings significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}.
 In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution.
@@
 
-The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy.
-That is to be expected because the position of each neighbour is already randomized, so there is virtually no difference between picking one of the first neighbours to copy and a random one among all.
-Seeing as the same conclusions apply to both the human and random strategies, we omit further analysis of the latter for simplicity.
-Both underperformed in comparison to evaluating the solutions according to number of filled cells.
-This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of social problem-solving.
-
-We have observed in our experiments that the progress of the solution, represented by the number of agents that solve the problem in a given round, follows a normal distribution.
-During the first few rounds no agents have found the solution.
-Then, in a moment that varies according to the particular instance of the problem, the first few agents solve the problem.
-From that point onwards the solution starts spreading through the network.
-As more agents obtain the complete solution, more likely it becomes that further agents will copy that solution from their neighbours, according to the conformist behaviour observed in~\cite{farenzena:collabem}.
-That leads the number of agents to obtain the solution to progressively increase in the following rounds, until it reaches a point where the few remaining agents take longer to obtain the solution due to factors such as being less capable solvers or being in unfavourable positions in the topology.
-
-We have run experiments in the four different topologies enumerated above, for 7 different problem instances, and obtained similar results in each.
-The progression of the solution for the \emph{Most Filled} and \emph{First Positions} strategies can be described as normal distributions of different mean and variance.
-In the context of the experiments, the mean indicates how soon the correct solution was found, and the variance how long it took to spread through the network.
-The exact values for those parameters vary widely according to factors such as topology and problem instance, but they follow a particular pattern.
-For all cases, the strategy that evaluated solutions had lower mean, indicating the solution was found sooner, and lower variance, meaning it spread faster.
-We have chosen the scale-free and 3-ring topologies as representative examples, and plotted the average of the results for a same instance of the problem for each in Figures~\ref{fig:sf_gauss} and~\ref{fig:ring_gauss}, respectively.
-In each can be seen the percentage of agents that find the correct solution in each round for the two strategies, with normal curves plotted over the values, evidencing the described behaviour.
-It's noticeable that the results fluctuate more for the second strategy, which is explained by its practically random method of choosing solutions to copy.
-
-In Figure~\ref{fig:global_gauss} the average for all experiments can be seen, encompassing every topology and instance.
-In this graph, the presence of the normal behaviour in the distribution is less clear, due to it combining several different instances and topologies.
-Nevertheless, its effects can still be seen.
-The \emph{Most Filled} strategy displays different residual peaks from particular instances, while the line for the \emph{First Positions} strategy starts flattening with the accumulation of several distributions from the individual experiments.
-Most importantly, the general result of a sooner finding and faster spreading of the correct solution for the first strategy endures, showing its consistency over different scenarios.
-
-Still, even though choosing a solution based on position instead of content is provably inefficient, that behaviour has been observed in human networks.
-In~\cite{farenzena:collabem} the authors suggest that it is justified in the real world because ``in a non-virtual environment, the feedback of the environment can cause an agent to stop communicating, e.g.
-in the case of injury or death'', so there would be no need for an agent to evaluate solutions because the environment is already selecting against ineffective ones.
-Since neither the original experiments nor our simulation included such a mechanism of natural selection, the advantages of that process have not been observed, but they might already be good enough that it would be unnecessary for the agents to have to spend effort evaluating the solutions.
-
-Another explanation might be that humans might find difficult evaluating sudoku partial solutions.
-Although we have used the number of filled cells as a metric, that is not guaranteed to accurately measure which solution is best, since individuals might fill in cells with the wrong value.
-That hypothesis is supported by the experiments of~\cite{mason:collablearnet}, which used optimization of a bidimensional function as the problem being solved.
+Although choosing a solution based on its position instead of content is provably inefficient, this behaviour has been observed in human networks~\cite{farenzena:collabem}.
+Perhaps this can be explained
+by humans finding it difficult to evaluate Sudoku partial solutions. 
+Although we have used the number of filled cells as a solution evaluation function, that is not guaranteed to accurately measure which solution is best, since individuals might fill in cells with the wrong value.
+That hypothesis is supported by the experiments of~\cite{mason:collablearnet}, which used optimization of a bi-dimensional function as the problem being solved.
 This problem has a straightforward and accurate method of determining the fitness of a solution, which is simply the value of the given function for the proposed coordinates.
-In this experiments, the subjects seemingly did effectively evaluate the proposed solutions, giving preference to the ones that were better evaluated.
+In their experiments, the subjects seemingly did effectively evaluate the proposed solutions, giving preference to the ones that were better evaluated.
 The difference in behaviour between the two experiments might be because in the latter the fitness of a certain solution was obvious to the agent, while in the former it's not as easy to pick the best solution out of the available ones.
@@
 Our experiments, however, have shown that although completeness is not necessarily an accurate measurement of quality, it was good enough to lead the network to the right solution.
-Not only that, it consistently performed better than the other strategies, even with high guess rates.
-%--Explain
-That means that the incorrect guesses were successfully filtered out, allowing the correct solutions to prevail.
-%--
 Those results might extend to other constraint satisfaction problems that don't have an accurate method of evaluation.
-Therefore, it is not necessary for the problem addressed to have an exact metric to compare different possible solutions.
-An imperfect metric is good enough to be employed in a problem-solving social network.
+Therefore, it is not necessary for the problem addressed to have an exact evaluation function to compare different possible solutions.
+An imperfect evaluation is good enough to be employed in a problem-solving social network.
 
-Also,~\cite{mason:collablearnet} differed in that each player had exactly three neighbours.
-That fact allowed the players to see all of their neighbours at the same time in the interface, and limit their attention to less data.~\cite{farenzena:collabem} suggests that future experiments might prefer to limit their topology to smaller degrees, seeing as subjects tend to not look beyond their first few neighbours.
-It is possible for the large number of neighbours to have discouraged an in-depth evaluation of the solutions by the players.
+\subsection{Copying and Guessing are Beneficial to the Algorithm's Performance}
 
-\subsection{Small Changes on the Interface Might Improve the Performance of Human Beings in Human Computation Environments}
+Regarding our hypothesis that a higher copy rate would be beneficial, our experiments indicate that in the topologies tested the copy rate indeed has a decisive role in enhancing the network's performance.
+To our surprise, however, they also indicate that guessing shows no signs of being detrimental to the process.
+On the contrary, in several cases it actually contributes to advancing the solution.
+We understand this is due to the fact that some low-level agents are incapable of solving some instances of the problem, not knowing the Sudoku solving rules needed to mark its cells.
+These agents have no hope of solving the problem individually without some guessing mechanism, and the high copy rates allow them to correct wrong guesses through copying better agents' solutions.
+What is particularly unexpected, however, is that the system did not seem to be detained by wrong guesses, even with high guess rates.
+This means that incorrect guesses were successfully filtered out, allowing the correct solutions to prevail.
+The agents seem to have been able to identify soon when a guess lead to an incorrect solution, eliminating it before it has a chance to spread.
+
+Comparing the results of the different copying strategies, it can also be observed that the copy rate has more influence over how fast the correct solution spreads through the network if the agents are evaluating their neighbour's solutions.
+The increase in performance of the network when copying increases is much faster for the \emph{Most Filled} strategy than for the \emph{First Positions} strategy, while increasing guessing has much less influence.
+These results confirm that the benefit of copying increases when the neighbours' solutions are evaluated.
+Meanwhile, when the agents don't evaluate the solutions they get less out of the act of copying, having to rely more on guessing to advance on their own.
+
+\subsection{Suggestions for the Design of Social Problem-Solving Systems}
 
@@
 One possibility is to display the evaluation of each solution to encourage players to copy the ones with better score.
-However, the SAT experiments from~\cite{farenzena:collabem} actually assigned a score to each solution displayed to the users, who nevertheless chose according to position rather than evaluation.
-Another possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead of using a pre-specified or random order.
+However, the SAT experiments from~\cite{farenzena:collabem} actually showed the score of each solution displayed to the users, who nevertheless chose according to position rather than evaluation.
+Another possibility is using the very behaviour of copying the first solutions to the system's advantage.
+By ordering the neighbours in the interface according to the quality of their solutions, with better-evaluated ones being displayed first, those will be copied more frequently.
+There is also the possibility suggested by~\cite{farenzena:collabem} of limiting the network's degree.
+Fewer connections allows for all neighbours to be displayed in the interface at once, without necessity of effort by the user by clicking buttons or scrolling.
+Moreover, humans might feel more encouraged to evaluate the solutions if they have fewer neighbours to choose from.
+That result is supported by~\cite{mason:collablearnet}, who limited the number of neighbours to three.
+In their experiments, the subjects seem to have indeed evaluated the neighbours' solutions, which might indicate this option to be promising.
 
-The limitation on the network's degree suggested by~\cite{farenzena:collabem} and employed by~\cite{mason:collablearnet} is also promising, and displays evidence of success.
-Fewer connections allows for all neighbours to be displayed in the interface at once, without necessity of effort by the user by clicking buttons or scrolling.
-Moreover, humans might feel more encouraged to evaluate their neighbours if the number of possible solutions is limited.
-%
-%\begin{figure}
-%\includegraphics[scale=0.45]{progression}
-%\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
-%}
-%\label{fig:progression}
-%\end{figure}
+Our results also show that a network benefits from higher rates of copying.
+One way to achieve that is to take advantage of a phenomenon presented in~\cite{mason:collablearnet}.
+It was observed that subjects copied more frequently when more than one neighbour shared the same solution.
+At the same time, higher local clustering in the network increased the probability that two neighbours of the same individual were also connected, which made more likely that the two neighbours shared the same solution.
+Therefore, by using topologies with higher clustering one can encourage human subjects to copy more.
 
@@
 
-We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments.
-To do this, we proposed a novel method for artificial social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}.
-We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems.
-We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes.
-With these results in mind, we conjectured that some properties of the graphic interface (as ordering the neighbours' solutions by the value of a evaluation function) could guide human subjects into the right direction, improving the performance of the social network.
-The validation of this hypothesis has been set as our future path and is currently being pursued.
+We have proposed a novel method for artificial social problem-solving that can be used to analyse the consequences of the behaviour observed in humans in collaborative networks.
+This is a general model that can be applied to simulate different social computing systems centered on diverse problems.
+Using it, we modelled the Sudoku-solving environment studied by~\cite{farenzena:collabem} and the behaviour of its subjects, in order to analyse their effects on the problem-solving process.
+We have discovered that, although humans seemed to choose a solution to copy based on its position on the interface, evaluating the neighbours' proposed solutions to select one for copying leads to the correct solution being found sooner and spreading faster throughout the network.
+Another important conclusion we have reached is that the performance of the network in solving the problem increases when agents copy more.
+Surprisingly, increasing the chance that the agents will guess when they cannot make a logical move is also beneficial, indicating that the network is successful in filtering incorrect solutions produced by guessing.
+
+With these results in mind, we have proposed some suggestions to improve the performance of a human social problem-solving network, using properties of the graphic interface and topology to encourage human subjects to follow more effective behaviour.
+In the future, it would be interesting to validate these suggestions through actual experiments with human beings.
+We also encourage the employment of the proposed method in simulating other experiments conducted with human subjects, using the results obtained to guide the design of new systems of social computation or the redesign of old ones.
 

### 2013-01-28 old stuff/Article.tex
Atualizei com a versão atual do artigo
Também organizei a estrutura de diretórios mais ou menos como
recomendado pelo Diego

--- 2013-01-27 Article.tex
@@
 \includegraphics[scale=1]{ijcai_sudoku/fill_iter}
-\caption{The graph shows the average number of iterations needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{Most Filled} strategy.
+\caption{The graph shows the average number of rounds needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{Most Filled} strategy.
 }
@@
 \includegraphics[scale=1]{ijcai_sudoku/first_iter}
-\caption{The graph shows the average number of iterations needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{First Positions} strategy.
+\caption{The graph shows the average number of rounds needed for all agents to obtain the correct solution, for a given value of copy rate and guess rate when using the \emph{First Positions} strategy.
 }
@@
 From our results for each topology, we plotted two surfaces for each strategy.
-The first shows the average number of iterations needed for the network to converge to the correct solution, and the second the number of experiments in which every agent obtained the correct solution in the limit of 100 rounds.
+The first shows the average number of rounds needed for the network to converge to the correct solution, and the second the number of experiments in which every agent obtained the correct solution in the limit of 100 rounds.
 
@@
 
-\subsection{Copying and Guessing are Beneficial to the Algorithm's Performance}
+\subsection{Copying and Guessing are Beneficial to the Network's Performance}
 
@@
 
-We have proposed a novel method for artificial social problem-solving that can be used to analyse the consequences of the behaviour observed in humans in collaborative networks.
-This is a general model that can be applied to simulate different social computing systems centered on diverse problems.
-Using it, we modelled the Sudoku-solving environment studied by~\cite{farenzena:collabem} and the behaviour of its subjects, in order to analyse their effects on the problem-solving process.
-We have discovered that, although humans seemed to choose a solution to copy based on its position on the interface, evaluating the neighbours' proposed solutions to select one for copying leads to the correct solution being found sooner and spreading faster throughout the network.
+Collaborative human computation is a growing area of interest as researchers are attracted to the human problem-solving abilities and strategies.
+However, although a lot of data about human social behaviour can be collected from experiments, it is still difficult to explain that behaviour and its consequences.
+Knowing the limitations of human strategies is needed to guide the design of social problem-solving systems.
+We have proposed a novel method for artificial social problem-solving that can be used to analyse the behaviour observed in humans in collaborative networks.
+This is a general model that can be applied to simulate different social computing systems centred on diverse problems.
+We used it to model one particular experiment, simulating the strategies employed by humans on it, and obtained a number of interesting results.
+We have discovered that, although humans seemed to choose a solution to copy based on its position on the interface, evaluating the neighbours' proposed solutions to select one for copying leads to the correct solution being found sooner and spreading faster throughout the network even if the evaluation function employed is naive.
 Another important conclusion we have reached is that the performance of the network in solving the problem increases when agents copy more.
@@
 With these results in mind, we have proposed some suggestions to improve the performance of a human social problem-solving network, using properties of the graphic interface and topology to encourage human subjects to follow more effective behaviour.
+These include displaying neighbours with better-evaluated solutions first, to encourage subjects to copy from them, and using topologies with higher local clustering, to encourage a higher frequency of copy.
+Future developers of collaborative systems can use these points to plan their design in order to take maximum advantage of the problem-solving network.
 In the future, it would be interesting to validate these suggestions through actual experiments with human beings.
